---
title: "01 — Build EDGAR Auditor Change Event File"
author: "Neil"
date: "`r Sys.Date()`"
output: html_document
---

# Overview

This script builds the auditor change event file from SEC EDGAR Form 8-K filings.

**Input:**  SEC EDGAR (downloaded via HTTP — no local raw file)
**Output:** `Data/Processed/auditor_changes_raw.parquet`

**Logic:**
1. Download EDGAR quarterly index files (2000–2023) and filter for 8-K filings.
2. Use EDGAR full-text search API (EFTS) to pre-filter filings that contain "Item 4.01"
   text, reducing the download set from ~800K filings to ~15K–25K.
3. For each candidate filing, download the primary document and extract the Item 4.01
   section via regex.
4. Parse the extracted text to capture: auditor out (departing), auditor in (incoming),
   reason code (dismissal vs. resignation), and whether disagreements were disclosed.
5. Write a clean parquet file to Data/Processed/.

**Notes on EDGAR rate limits:**
SEC limits automated requests to 10 requests/second. This script enforces a 0.15-second
delay between requests. For the full 2000–2023 run (~20K filings), expect ~45 min runtime.
Run in a non-interactive session (e.g., Rscript -e "rmarkdown::render(...)").

```{r setup, message=FALSE, warning=FALSE}
library(httr2)
library(dplyr)
library(readr)
library(stringr)
library(arrow)
library(lubridate)
library(purrr)

# ── User-configurable parameters ──────────────────────────────────────────────
START_YEAR   <- 2000L
END_YEAR     <- 2023L
OUT_FILE     <- here::here("Data/Processed/auditor_changes_raw.parquet")
LOG_FILE     <- here::here("Data/Processed/01_edgar_parse_log.csv")
REQUEST_DELAY <- 0.15   # seconds between EDGAR requests (stay under 10 req/sec)
USER_AGENT   <- "Research project — contact: neilh@example.com"  # SEC requires this
# ──────────────────────────────────────────────────────────────────────────────

# Helper: polite GET with retry
edgar_get <- function(url, n_retry = 3, ...) {
  for (i in seq_len(n_retry)) {
    Sys.sleep(REQUEST_DELAY)
    resp <- tryCatch(
      request(url) |>
        req_headers(`User-Agent` = USER_AGENT) |>
        req_timeout(30) |>
        req_perform(),
      error = function(e) NULL
    )
    if (!is.null(resp) && resp_status(resp) == 200) return(resp)
    Sys.sleep(2^i)  # exponential back-off on failure
  }
  NULL  # return NULL if all retries fail
}
```

---

## Step 1: Build the 8-K filing index via EDGAR quarterly indexes

EDGAR publishes a `company.gz` (or `full-index/company.idx`) file each quarter listing
every filing. We filter for form type `8-K` and `8-K/A`.

```{r build-index}
# Construct list of quarterly index URLs
quarters <- expand.grid(
  year    = START_YEAR:END_YEAR,
  quarter = 1:4
) |>
  arrange(year, quarter) |>
  mutate(
    url = sprintf(
      "https://www.sec.gov/Archives/edgar/full-index/%d/QTR%d/company.idx",
      year, quarter
    )
  )

# Download and parse each quarterly index — keep only 8-K rows
parse_quarter_index <- function(url) {
  resp <- edgar_get(url)
  if (is.null(resp)) {
    message("Failed: ", url)
    return(NULL)
  }
  raw <- resp_body_string(resp)
  lines <- str_split_1(raw, "\n")
  # The company.idx format: Company Name | Form Type | CIK | Date Filed | Filename
  # Header lines start with "Company" or dashes; data lines are fixed-width
  data_lines <- lines[nchar(lines) > 50 & !str_detect(lines, "^Company|^-")]
  if (length(data_lines) == 0) return(NULL)

  # Parse fixed-width: columns break at positions used by SEC
  # Format: col1=0-62 (company), col2=62-74 (form type), col3=74-86 (CIK),
  #         col4=86-98 (date filed), col5=98+ (filename)
  df <- tibble(raw = data_lines) |>
    mutate(
      company_name = str_trim(str_sub(raw, 1,  62)),
      form_type    = str_trim(str_sub(raw, 63, 74)),
      cik          = str_trim(str_sub(raw, 75, 86)),
      date_filed   = str_trim(str_sub(raw, 87, 98)),
      filename     = str_trim(str_sub(raw, 99, nchar(raw)))
    ) |>
    select(-raw) |>
    filter(form_type %in% c("8-K", "8-K/A"))

  df
}

message("Downloading quarterly indexes: ", nrow(quarters), " quarters")
index_list <- map(quarters$url, parse_quarter_index, .progress = TRUE)
index_8k   <- bind_rows(compact(index_list))

message("Total 8-K filings in index: ", nrow(index_8k))
```

---

## Step 2: Pre-filter for Item 4.01 using EDGAR EFTS

The EDGAR full-text search system (EFTS) lets us query for filings whose full text
contains a specific string. We query for `"4.01"` among 8-K form types to identify
filings that are likely auditor change disclosures before downloading their text.

This reduces the download set from ~800K filings to ~20K.

```{r efts-prefilter}
# EFTS returns JSON with filing accession numbers. Paginate through results.
fetch_efts_page <- function(start_dt, end_dt, from = 0, size = 200) {
  url <- sprintf(
    paste0(
      "https://efts.sec.gov/LATEST/search-index?",
      "q=%%224.01%%22&forms=8-K,8-K%%2FA",
      "&dateRange=custom&startdt=%s&enddt=%s",
      "&from=%d&hits.hits._source.period_of_report=true&hits.hits.total=true"
    ),
    start_dt, end_dt, from
  )
  resp <- edgar_get(url)
  if (is.null(resp)) return(NULL)
  jsonlite::fromJSON(resp_body_string(resp), simplifyVector = FALSE)
}

# Fetch all EFTS results year by year (EFTS caps at 10K results per query window)
collect_efts_accessions <- function(year) {
  start_dt <- sprintf("%d-01-01", year)
  end_dt   <- sprintf("%d-12-31", year)

  # First call to get total count
  first <- fetch_efts_page(start_dt, end_dt, from = 0, size = 1)
  if (is.null(first)) return(character(0))
  total <- first$hits$total$value %||% 0
  if (total == 0) return(character(0))

  from_vals <- seq(0, min(total - 1, 9800), by = 200)
  accessions <- character(0)

  for (from in from_vals) {
    page <- fetch_efts_page(start_dt, end_dt, from = from, size = 200)
    if (is.null(page$hits$hits)) next
    hits <- page$hits$hits
    acc  <- vapply(hits, function(h) h$`_id`, character(1))
    accessions <- c(accessions, acc)
  }
  unique(accessions)
}

message("Running EFTS pre-filter by year...")
efts_by_year <- map(START_YEAR:END_YEAR, collect_efts_accessions, .progress = TRUE)
names(efts_by_year) <- as.character(START_YEAR:END_YEAR)
efts_accessions <- unlist(efts_by_year, use.names = FALSE)

message("EFTS pre-filter: ", length(efts_accessions), " candidate filings with '4.01'")

# Convert accession numbers to the filename format used in the quarterly index
# Accession format: XXXXXXXXXX-YY-ZZZZZZ  → CIK/XXXXXXXXXX-YY-ZZZZZZ.txt
# In the index, filename looks like: edgar/data/{CIK}/{acc-nodash}.txt
# Normalise accessions from EFTS (may be with or without dashes)
efts_acc_nodash <- str_remove_all(efts_accessions, "-")
```

---

## Step 3: Intersect EFTS candidates with the index

```{r intersect}
# Add accession number (no dashes) to the index table for joining
index_8k <- index_8k |>
  mutate(
    acc_nodash = str_remove_all(
      basename(tools::file_path_sans_ext(filename)), "-"
    )
  )

# Some EFTS accession numbers include dashes; derive nodash version
candidates <- index_8k |>
  filter(acc_nodash %in% efts_acc_nodash)

message("Candidates after intersection: ", nrow(candidates))
```

---

## Step 4: Download and parse Item 4.01 text for each candidate filing

```{r parse-filings, message=FALSE}
# Build full document URL from the index filename
# Index filename format: "edgar/data/{cik}/{accession-nodash}-index.htm"
# Full text submission file:  edgar/data/{cik}/{accession-nodash}.txt
# But the most reliable approach is to read the filing index page and find
# the primary document link.

# Extract accession number with dashes (needed in URLs)
acc_with_dashes <- function(acc_nodash) {
  # Format: XXXXXXXXXX-YY-ZZZZZZ (10-2-6)
  paste0(
    str_sub(acc_nodash, 1, 10), "-",
    str_sub(acc_nodash, 11, 12), "-",
    str_sub(acc_nodash, 13, 18)
  )
}

# Get the filing index page and return the URL of the primary document
get_primary_doc_url <- function(cik, acc_nodash) {
  acc_dashes <- acc_with_dashes(acc_nodash)
  index_url  <- sprintf(
    "https://www.sec.gov/Archives/edgar/data/%s/%s/%s-index.htm",
    cik, acc_nodash, acc_dashes
  )
  resp <- edgar_get(index_url)
  if (is.null(resp)) return(NA_character_)

  html_text <- resp_body_string(resp)
  # Look for the primary document link (usually the .htm or .txt 8-K body)
  # The index table lists document type "8-K" or "8-K/A" in the Description column
  # Regex: find href in a table row that contains "8-K" form type
  links <- str_match_all(
    html_text,
    '<a href="(/Archives/edgar/data/[^"]+\\.(?:htm|txt))"[^>]*>[^<]*</a>'
  )[[1]]

  if (nrow(links) == 0) return(NA_character_)
  # Return first match — typically the primary document
  paste0("https://www.sec.gov", links[1, 2])
}

# Extract the Item 4.01 section from 8-K full text
# Returns a list: list(item401_text, auditor_out, auditor_in, reason, disagreements)
extract_item401 <- function(text) {
  if (is.na(text) || nchar(text) == 0) return(NULL)

  # Remove HTML tags if present
  clean <- str_replace_all(text, "<[^>]+>", " ")
  clean <- str_replace_all(clean, "&nbsp;", " ")
  clean <- str_replace_all(clean, "&#[0-9]+;", " ")
  clean <- str_squish(clean)

  # Find Item 4.01 section — look for "Item 4.01" or "ITEM 4.01"
  # Section ends at next "Item X.XX" header or end of document
  pattern_start <- regex("Item\\s+4\\.01", ignore_case = TRUE)
  pattern_end   <- regex("Item\\s+[0-9]+\\.[0-9]+", ignore_case = TRUE)

  start_pos <- str_locate(clean, pattern_start)
  if (is.na(start_pos[1])) return(NULL)  # No Item 4.01 found

  # Find next item after this one
  after_start <- str_sub(clean, start_pos[1] + 10L)
  end_match   <- str_locate(after_start, pattern_end)

  if (!is.na(end_match[1]) && end_match[1] > 5) {
    item_text <- str_sub(after_start, 1, end_match[1] - 1L)
  } else {
    # No subsequent item found — take up to 3000 chars
    item_text <- str_sub(after_start, 1, 3000L)
  }
  item_text <- str_squish(item_text)
  if (nchar(item_text) < 20) return(NULL)

  # ── Parse auditor names ────────────────────────────────────────────────────
  # Departing auditor: usually mentioned as "dismissed", "resigned", "replaced",
  # "former independent registered public accounting firm", or simply named first.
  # Common patterns:
  #   "dismissed [Auditor Name]"
  #   "[Auditor Name] has been dismissed"
  #   "[Auditor Name] resigned"
  #   "formerly served as ... [Auditor Name]"
  #   "engagement of [New Auditor]"

  # We use a set of known audit firm names as anchors
  big4      <- c("Deloitte", "PricewaterhouseCoopers", "PwC", "Ernst & Young",
                 "EY", "KPMG", "Grant Thornton", "BDO", "RSM", "McGladrey",
                 "Moss Adams", "Dixon Hughes", "Crowe", "Eide Bailly")
  firm_pat  <- paste(big4, collapse = "|")

  # Dismissal vs resignation
  reason <- case_when(
    str_detect(item_text, regex("dismiss|terminat|replac", ignore_case = TRUE)) ~ "dismissal",
    str_detect(item_text, regex("resign|declin|withdrew", ignore_case = TRUE))  ~ "resignation",
    TRUE ~ "unclassified"
  )

  # Disagreements disclosed?
  disagreements <- str_detect(
    item_text,
    regex("disagreement|disagree", ignore_case = TRUE)
  )

  # Auditor out: firm named in context of departure
  out_match <- str_match(
    item_text,
    regex(
      paste0("(", firm_pat, ")[^.]{0,200}(dismiss|terminat|replac|resign|former|previous)"),
      ignore_case = TRUE
    )
  )
  auditor_out <- if (!is.na(out_match[1, 2])) str_trim(out_match[1, 2]) else NA_character_

  # Auditor in: firm named in context of engagement/appointment
  in_match <- str_match(
    item_text,
    regex(
      paste0("(engag|appoint|retain|select|hired)[^.]{0,100}(", firm_pat, ")"),
      ignore_case = TRUE
    )
  )
  auditor_in <- if (!is.na(in_match[1, 3])) str_trim(in_match[1, 3]) else NA_character_

  list(
    item401_text  = item_text,
    auditor_out   = auditor_out,
    auditor_in    = auditor_in,
    reason        = reason,
    disagreements = disagreements
  )
}

# Main parsing loop
parse_one_filing <- function(row) {
  cik        <- row$cik
  acc_nodash <- row$acc_nodash
  date_filed <- row$date_filed
  company    <- row$company_name

  # Get primary document URL
  doc_url <- get_primary_doc_url(cik, acc_nodash)
  if (is.na(doc_url)) {
    return(tibble(
      cik = cik, acc_nodash = acc_nodash, date_filed = date_filed,
      company_name = company, parse_status = "no_doc_url",
      item401_text = NA, auditor_out = NA, auditor_in = NA,
      reason = NA, disagreements = NA
    ))
  }

  # Download primary document
  resp <- edgar_get(doc_url)
  if (is.null(resp)) {
    return(tibble(
      cik = cik, acc_nodash = acc_nodash, date_filed = date_filed,
      company_name = company, parse_status = "download_failed",
      item401_text = NA, auditor_out = NA, auditor_in = NA,
      reason = NA, disagreements = NA
    ))
  }

  doc_text <- resp_body_string(resp)
  result   <- extract_item401(doc_text)

  if (is.null(result)) {
    return(tibble(
      cik = cik, acc_nodash = acc_nodash, date_filed = date_filed,
      company_name = company, parse_status = "no_item401_found",
      item401_text = NA, auditor_out = NA, auditor_in = NA,
      reason = NA, disagreements = NA
    ))
  }

  tibble(
    cik           = cik,
    acc_nodash    = acc_nodash,
    date_filed    = date_filed,
    company_name  = company,
    parse_status  = "ok",
    item401_text  = result$item401_text,
    auditor_out   = result$auditor_out,
    auditor_in    = result$auditor_in,
    reason        = result$reason,
    disagreements = result$disagreements
  )
}

# ── Run the parser ─────────────────────────────────────────────────────────────
# Split candidates into rows for iteration
candidate_rows <- candidates |>
  select(cik, acc_nodash, date_filed, company_name) |>
  mutate(row_id = row_number())

message("Parsing ", nrow(candidate_rows), " candidate filings...")
results_list <- map(
  seq_len(nrow(candidate_rows)),
  function(i) {
    if (i %% 500 == 0) message("  Processed: ", i, " / ", nrow(candidate_rows))
    parse_one_filing(candidate_rows[i, ])
  },
  .progress = FALSE  # manual progress above
)

parsed <- bind_rows(results_list)
message("Parse complete. Status breakdown:")
print(table(parsed$parse_status))
```

---

## Step 5: Clean and write output

```{r clean-output}
# Keep only successfully parsed rows with confirmed Item 4.01 content
auditor_changes <- parsed |>
  filter(parse_status == "ok") |>
  mutate(
    date_filed  = ymd(date_filed),
    filing_year = year(date_filed),
    # Classify Big 4 involvement
    out_big4 = str_detect(
      auditor_out,
      regex("Deloitte|PricewaterhouseCoopers|PwC|Ernst & Young|EY|KPMG",
            ignore_case = TRUE)
    ),
    in_big4  = str_detect(
      auditor_in,
      regex("Deloitte|PricewaterhouseCoopers|PwC|Ernst & Young|EY|KPMG",
            ignore_case = TRUE)
    ),
    # Direction of change
    quality_direction = case_when(
      out_big4 & !in_big4 ~ "Big4_to_nonBig4",
      !out_big4 & in_big4 ~ "nonBig4_to_Big4",
      out_big4 & in_big4  ~ "Big4_to_Big4",
      TRUE                 ~ "nonBig4_to_nonBig4"
    )
  ) |>
  arrange(date_filed)

# Write full parse log (including failures) for diagnostic review
write_csv(parsed, LOG_FILE)
message("Parse log written to: ", LOG_FILE)

# Write clean event file
write_parquet(auditor_changes, OUT_FILE)
message("Auditor change event file written to: ", OUT_FILE)
message("Rows: ", nrow(auditor_changes))
message("Date range: ", min(auditor_changes$date_filed), " — ",
        max(auditor_changes$date_filed))

# Quick summary
auditor_changes |>
  count(filing_year, quality_direction) |>
  tidyr::pivot_wider(names_from = quality_direction, values_from = n, values_fill = 0L) |>
  print(n = 30)
```

---

## Session notes

- **Next script** (02): Merge event file with CRSP returns and volume to compute CARs
  and abnormal volume around the `[-1, +1]` window.
- **Known limitations of this parser:**
  - Auditor name extraction relies on a list of ~15 large firm names. Smaller regional
    firms will show `NA` for `auditor_out`/`auditor_in` — these rows are still useful for
    volume/CAR analysis; the auditor-name fields are used only for subgroup tests.
  - The regex-based section extractor may fail on unusual 8-K HTML formatting (e.g.,
    heavily nested tables). Such cases are logged as `no_item401_found`.
  - EDGAR amended filings (`8-K/A`) are included; review whether to drop them in 02.
