\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{natbib}
\usepackage{booktabs}
\usepackage{hyperref}

\title{Political Polarization and Market Reactions to Auditor-Change Disclosures}
\author{Neil Hwang\\
        \small Bronx Community College, CUNY}
\date{\today}

% Hypothesis environment
\newtheorem{hyp}{Hypothesis}
\newtheorem{proposition}{Proposition}

\begin{document}
\maketitle
\doublespacing

% ── Abstract ─────────────────────────────────────────────────────────────────

\begin{abstract}
We provide the first evidence that political polarization is associated
with stronger investor reactions to mandatory audit-related disclosures. Auditor-change
filings (Form~8-K Item~4.01) require the firm to disclose the circumstances
of the separation, but the signal can be ambiguous --- investors must assess
auditor credibility and infer the nature of the change, judgments that
depend on trust in auditors and the PCAOB as regulatory institutions.
Because trust in auditors and regulatory institutions may vary with
political identity, political polarization may be associated with more
heterogeneous interpretations of the same public filing. In a sample of
678 auditor-change disclosures (2001--2023), firms headquartered in more
politically polarized states experience significantly larger abnormal
trading volume ($p = 0.010$) and absolute abnormal returns ($p = 0.039$)
around the filing. The effect is absent for the same firms' earnings
announcements (AbVol $p = 0.393$; $|CAR|$ $p = 0.918$; $N = 20{,}800$),
consistent with the idea that polarization is associated with greater
disagreement when the disclosure requires interpretation, not when the
signal is numerically precise.
These findings suggest a limit to disclosure-based regulation: when
investors differ in their assessments of institutional credibility, the
same mandatory disclosure can generate more, not less, disagreement.
\end{abstract}

% ── 1. Introduction ───────────────────────────────────────────────────────────

\section{Introduction}
\label{sec:intro}

Auditor-change disclosures are among the most tightly regulated content-specific
disclosures in the Form~8-K system. Form~8-K Item~4.01 and the related
Regulation~S-K Item~304 require the registrant to disclose whether the
auditor resigned or was dismissed, any disagreements with the departing
auditor over accounting principles or auditing procedures, any reportable
events concerning the reliability of prior audits or internal controls, and
whether the audit committee approved the change. The former auditor must
furnish a concurrence letter to the SEC. This disclosure regime is
\emph{about} the audit function: it reveals information about the credibility
of the firm's financial reporting gatekeeper at a specific moment of
separation. Prior research establishes that these disclosures move prices:
abnormal returns around auditor changes reflect investor assessments of
reporting quality, audit risk, and the nature of the separation
\citep{johnson1990, dodd1984, defond1998, shu2000, landsman2009,
whisenant2003, hennes2014}. Yet the magnitude of market reactions varies
substantially across otherwise similar filings, and the sources of that
cross-sectional variation remain incompletely understood. This paper
documents a previously unexplored correlate: the political-information
environment in which investors interpret the disclosure. We find that
market reactions to Item~4.01 filings are larger where the firm's
headquarters state is more politically divided, consistent with investors
holding more heterogeneous priors about audit credibility and regulatory
oversight of the audit function.

Item~4.01 disclosures are distinctive among mandatory filings for three
reasons that make them a natural accounting research laboratory. First,
the content is \emph{regulated}: unlike press releases or management forecasts,
Reg~S-K Item~304 prescribes what must be disclosed, and the former auditor
must respond in writing. This removes the confound of selective disclosure
and standardizes the information set across firms. Second, the signal is
\emph{about audit credibility}: investors are asked to update their beliefs
about the reliability of the firm's reporting gatekeeper, not about a
typical earnings surprise. Assessing that update requires investors to
evaluate the credibility of the departing auditor, the incoming auditor,
and the regulatory infrastructure --- the PCAOB, audit standards, and the
broader institutional apparatus that underwrites audit quality. Third,
the signal is \emph{inherently ambiguous}: firms may change auditors for
reasons ranging from routine fee negotiation to concealed disagreements
over financial reporting, and the filing frequently provides incomplete
guidance about which explanation applies \citep{boone2001, beneish2005}.
Investors must form their own interpretation. Together, these features make
Item~4.01 a uniquely diagnostic setting for studying how investor beliefs
about audit credibility shape the informativeness of mandatory audit
disclosure.

Our theoretical framework builds on \citet{kandel1995}: investors observe the
same public audit signal but form different posteriors depending on their priors
about firm quality, auditor credibility, and the reliability of regulatory oversight.
Political polarization amplifies this heterogeneity. Polarized investors diverge
not only in their substantive interpretations of an auditor change --- whether
it signals earnings manipulation risk or routine governance --- but also in
their assessments of whether auditors and the PCAOB are credible certifiers
of financial reporting quality. This divergence is distinct from information
asymmetry: polarization does not change what is disclosed, only how investors
with different priors process it. Under standard belief-driven trading models
\citep{harris1993}, greater posterior dispersion translates into higher abnormal
volume and larger absolute price movements around the disclosure.

We identify this effect using cross-state variation in partisan polarization,
measured as one minus the absolute two-party presidential vote margin at the
state level, constructed from MIT Election Lab county-level returns and
forward-filled to annual frequency.
We use presidential rather than congressional returns because presidential
elections are the most nationalized arena of U.S. electoral competition ---
outcomes are driven by broad national partisan forces rather than candidate-
or district-specific factors --- making them a cleaner proxy for the partisan
belief environment \citep{vertz1987, abramowitz2016, moskowitz2021}.
More polarized states --- where the presidential electorate is more evenly
divided between the parties --- capture political-information environments in
which investors may be more likely to hold divergent priors about institutional
credibility and the interpretation of regulatory signals. We acknowledge a key
limitation of this proxy: institutional investors are geographically dispersed
and need not share the political characteristics of the firm's headquarters
state. We treat headquarters-state partisan polarization as a noisy
reduced-form proxy for the political-information environment surrounding the
disclosure, not a precise measure of individual
investor beliefs; measurement error
of this kind attenuates estimated coefficients toward zero, so our findings are
likely conservative. Our sample consists of 678 Form~8-K Item~4.01 filings from
2001 to 2023, matched to CRSP daily return and volume data and Compustat firm
characteristics. Our main specification regresses abnormal
trading volume and $|CAR[-1,+1]|$ on standardized partisan polarization, controlling for firm size,
leverage, profitability, and book-to-market ratio, with year and industry
fixed effects throughout.

We find that firms headquartered in more politically polarized states experience
significantly larger abnormal trading volume ($p = 0.010$) and absolute abnormal
returns ($p = 0.039$) around auditor-change disclosures. A within-firm placebo
test on the same firms' earnings announcements ($N = 20{,}800$) is
inconsistent with a generic salience explanation. The volume result is robust to three alternative
polarization proxies, alternative clustering structures, and a small-firm
subsample restriction; the absolute return result is more fragile across proxies,
consistent with volume being the sharper formal prediction. Post-event returns
show no reversal, indicating persistent belief heterogeneity rather than
transient overreaction.

This paper makes three contributions to the auditing and audit-disclosure
literatures. First, we document a new correlate of cross-sectional variation
in market reactions to auditor-change disclosures. A long literature in
accounting documents that auditor-change 8-Ks are informative events
\citep{johnson1990, dodd1984, defond1998, shu2000, landsman2009,
whisenant2003, hennes2014}, but that work focuses on whether the signal
conveys information on average and how its content varies across event
types. We show that market reactions to the same Item~4.01 filing
are systematically associated with the political composition of the local
information environment --- an economically meaningful source of variation
in the effectiveness of this specific mandatory disclosure regime that is
not captured by existing firm-level or event-type moderators.
Second, we isolate audit-credibility-based interpretation from generic
attention effects. Two within-firm placebo tests show that
headquarters-state polarization has no detectable effect on market
reactions to the same firms' earnings announcements ($N = 20{,}800$) or
officer-change (Item~5.02) disclosures ($N = 3{,}677$), while pooled
specifications confirm that the polarization effect is significantly
larger for auditor-change disclosures than for either placebo event
type. The officer-change placebo is especially tight: both event types
are mandatory 8-K filings requiring investors to infer the nature of the
change from limited disclosure, but only auditor changes involve
institutional trust in auditors and the PCAOB.
Together, these patterns are more consistent with heterogeneous
interpretation of a credibility-sensitive audit signal than with a
purely generic-attention account.
Third, our findings bear directly on disclosure-based regulation of
auditing. The SEC and PCAOB rely heavily on mandatory disclosure as a
regulatory tool --- Item~4.01, critical audit matters under AS~3101,
going-concern opinions, and internal control reports are all instances of
the same regulatory model. Our results suggest that the effectiveness of
this model in conveying information varies with the political-information
environment in which investors interpret the disclosure, with the
effect operating on a credibility dimension that is not typically
measured in standard audit-quality assessments.

The remainder of the paper proceeds as follows. Section~\ref{sec:lit} reviews
the related literature. Section~\ref{sec:theory} develops the theoretical
framework. Section~\ref{sec:hypotheses} states the testable hypotheses.
Section~\ref{sec:design} describes the empirical design. Section~\ref{sec:results}
presents the results. Section~\ref{sec:conclusion} concludes.

% ── 2. Related Literature ─────────────────────────────────────────────────────

\section{Related Literature}
\label{sec:lit}

\subsection{Audit Reports and Capital Markets}

A substantial literature documents that auditor-related disclosures convey
information to investors. Early studies show that qualified audit opinions affect
stock prices \citep{firth1978, dodd1984}. Subsequent work examines how audit
quality relates to market outcomes more broadly \citep{francis2004, defond2014}.
Research on expanded audit reporting --- including critical audit matters under
PCAOB AS~3101 --- finds mixed evidence on incremental informativeness, with some
studies finding that richer disclosures affect investor decisions
\citep{christensen2014} and others finding limited price effects
\citep{gutierrez2018}. We build on this literature by asking not whether audit
signals are informative in the aggregate, but whether their interpretation varies
systematically with the political environment.

\subsection{Auditor Changes}

The accounting literature has studied auditor changes for four decades,
beginning with \citet{dodd1984}, who document that investors respond
differentially to auditor changes depending on the disclosed circumstances
of the separation. \citet{johnson1990} show that voluntary auditor changes
reveal information about the audit market, and that Big-8 departures
generate negative abnormal returns while Big-8 appointments are viewed more
favorably. \citet{defond1998} find that discretionary accruals increase
around auditor changes in directions consistent with opinion shopping.
\citet{shu2000} identifies the particular informativeness of
\emph{resignations}, showing that voluntarily departing auditors signal
elevated client risk that investors partially price at the filing date.
\citet{boone2001} extend this finding to trading activity, documenting that
resignations generate abnormal retail trading and reduced liquidity.
\citet{beneish2005} ask whether resignation filings reduce uncertainty
about reporting quality and conclude that they do not, because the language
of the filing often leaves investors without sharp information about the
cause of the separation. \citet{whisenant2003} examine the specific
content of Item~304 disclosures --- disagreements, reportable events, and
auditor concurrence letters --- and show that the market responds to the
disclosed content beyond the fact of the change.
\citet{landsman2009} characterize auditor switching in the post-Enron
environment and show that the identity of the outgoing and incoming auditor
conveys information about client risk realignment. More recently,
\citet{hennes2014} show that auditor dismissals after accounting
restatements have significant market consequences and signal different
things than resignations.

This literature establishes that auditor-change disclosures are informative
events and that the content of the filing --- who departed, who replaced
them, and the stated reason --- matters for market reactions. What this
literature does not examine, and what we add, is a dimension of
\emph{cross-sectional heterogeneity in the interpretation} of the same
Item~4.01 filing: whether two investors receiving the same disclosure form
the same posterior about the firm's audit quality. Our contribution is
to show that market reactions are systematically associated with the political
composition of the local information environment, providing a new lens on
the conditions under which Item~4.01 disclosures generate trading and
price movement.

\subsection{Political Economy of Auditing}

A related literature examines how political factors influence audit outcomes.
\citet{chan2006} document that political connections shape auditor reporting
behavior and auditor switching in a cross-country setting, showing that audit
opinions respond to political incentives rather than purely economic ones.
More broadly, the political economy of auditing encompasses how regulatory,
institutional, and political pressures shape the supply of audit quality
\citep{francis2004, defond2014}. \citet{lennox2010} show that Big~4 auditor
oversight is associated with lower fraud incidence, underscoring that the
institutional infrastructure surrounding auditing --- including regulatory
design and oversight --- has measurable consequences for financial reporting
quality.

Our paper examines a different and largely unexplored dimension: the
\emph{investor side} of the audit signal. This mechanism is particularly
salient in the context of PCAOB oversight, whose authority and credibility
as a regulatory body may not be assessed uniformly across investor groups.
Investors who are more skeptical of regulatory institutions --- consistent
with evidence that political identity systematically shapes financial
attitudes and behavior \citep{kempf2024} --- may discount the credibility
of auditor disclosures differently from investors who trust regulatory
oversight. This mechanism is orthogonal to
the auditor-side political economy literature and complements it: even if
political pressures leave auditor behavior unchanged, polarization in the
investor population can amplify the capital-market consequences of those
disclosures.

\subsection{Political Polarization and Capital Markets}
\label{sec:pol_markets}

A growing literature documents that partisan identity influences investor
behavior and beliefs \citep{kempf2024, gerberhuber2009, coibion2020,
barrioshochberg2021}, and that politically slanted media coverage can
generate disagreement and trading volume for politically salient firms
\citep{goldmanetal2024}. We differ from this literature in two ways.
First, our information set is a standardized mandatory filing received
identically by all investors, not media-intermediated coverage. Second,
the setting is audit disclosure, where the object of investor belief is
not a partisan policy outcome but the credibility of a regulated
gatekeeper relationship. This matters because institutional trust in
auditors and the PCAOB varies with political identity
\citep{iyengar2019}, so the same Item~4.01 filing can generate divergent
posteriors about audit quality even when investors agree on the
underlying facts of the change.

\subsection{Heterogeneous Beliefs and Trading}

Our theoretical framework draws on models of heterogeneous beliefs in financial
markets. \citet{harris1993} show that differences of opinion generate trade even
without private information. \citet{kandel1995} demonstrate that investors with
heterogeneous priors interpret identical public signals differently, generating
trading volume and price effects. \citet{hong2007} survey the broader literature
on disagreement and asset prices. We contribute to this literature by linking
belief heterogeneity to a specific, measurable source --- political polarization
--- and by identifying the audit disclosure setting as a clean empirical context.

% ── 3. Theory ─────────────────────────────────────────────────────────────────

\section{Theory}
\label{sec:theory}

We formalize polarization as a latent force that increases heterogeneity in
investors' interpretation of auditor-originated disclosures. The Bayesian model
that follows operationalizes this heterogeneity through prior beliefs, which is
the most tractable formal channel. Institutional trust and perceived signal
precision should be understood as reduced-form sources of prior-like
heterogeneity: a less trusting investor effectively places a lower prior on the
informativeness of the auditor's signal; an investor who perceives lower signal
precision effectively flattens the likelihood function. Either way, the
formal result is the same increase in posterior dispersion. The model thus provides a microfoundation for the broader mechanism
described in the introduction, not a claim that priors are the only operative
channel.

In the affective-polarization literature \citep{iyengar2012,
iyengar2019}, partisan identity and out-party distrust shape how individuals
evaluate the credibility of information and the institutions that produce it.
In the present setting, these forces can be interpreted as widening the
cross-group gap in trust in the disclosure ($\tau_g$) or in perceived
signal precision ($\kappa_g$). As shown in Appendix~\ref{app:proofs}, all
three channels generate the same posterior-dispersion comparative static:
whenever polarization widens the cross-group posterior log-odds index, belief
dispersion and disagreement-sensitive market outcomes strictly increase. The
heterogeneous-priors model below should therefore be read as a tractable
benchmark case of this broader class of polarization mechanisms.

\subsection{Setting}

The model draws on the heterogeneous-priors framework of \citet{kandel1995}.
Consider a firm whose true quality $\theta \in \{0, 1\}$ is unknown to
investors. The firm discloses an auditor-related signal $s \in \{0, 1\}$ (e.g.,
an auditor change announcement). Signals are informative: $P(s=1 \mid
\theta=1) = p_H > P(s=1 \mid \theta=0) = p_L$, with $p_H > p_L$.

Investors observe $s$ and form posterior beliefs. All investors share the
same likelihood function $\{p_H, p_L\}$ but differ in their prior beliefs
about the firm's quality.

\textbf{Two-group structure.} We model investors as belonging to two
ideological groups indexed by political affiliation $g \in \{D, R\}$, with
population shares $\omega_D$ and $\omega_R = 1 - \omega_D$. Group $g$ holds
prior $\pi_g \equiv P_g(\theta = 1) \in (0,1)$, with $\pi_D \neq \pi_R$.
Group-level priors reflect differential trust in auditors and regulatory
institutions. In the model, all heterogeneity is captured by differences
in $\pi_g$; in practice, polarization may also affect how investors perceive
signal precision ($p_H, p_L$) or how much weight they place on the disclosure
relative to their priors. The reduced-form predictions are the same: greater
political distance generates greater dispersion in posterior beliefs.
Polarization increases the \emph{dispersion} of priors across groups without
changing the \emph{average} prior.

\subsection{Belief Updating}

Group $g$'s posterior belief after observing $s=1$ is:
\begin{equation}
    \label{eq:bayes}
    P_g(\theta = 1 \mid s = 1)
    = \frac{p_H \, \pi_g}{p_H \, \pi_g + p_L (1 - \pi_g)}
    \equiv \phi(\pi_g).
\end{equation}
The function $\phi(\cdot)$ is strictly increasing in $\pi_g$. It is also concave
(since $\phi''(\pi) < 0$ for all $\pi \in (0,1)$ when $p_H > p_L$); concavity
implies that a mean-preserving spread of priors shifts the average posterior
downward, which has implications for equilibrium prices, but it is not required
for the variance result below, which depends only on strict monotonicity.

We now establish the central comparative static of the model: that any
widening of the gap between group priors --- holding the average prior
fixed --- increases the dispersion of posterior beliefs. This is the
formal sense in which polarization amplifies disagreement.

\begin{proposition}[Polarization and belief dispersion]
    \label{prop:dispersion}
    Fix population shares $\omega_D, \omega_R > 0$ with $\omega_D + \omega_R = 1$ and mean prior
    $\bar{\pi} = \omega_D \pi_D + \omega_R \pi_R$. The variance of posterior beliefs
    across groups is
    \[
        \mathrm{Var}[\phi(\pi_g)]
        = \omega_D \omega_R \bigl(\phi(\pi_D) - \phi(\pi_R)\bigr)^2.
    \]
    For any increase in $|\pi_D - \pi_R|$ that holds $\bar{\pi}$ fixed,
    $\mathrm{Var}[\phi(\pi_g)]$ strictly increases.
\end{proposition}

\noindent\textit{Proof.} See Appendix~\ref{app:proofs}. $\square$

\medskip
\noindent\textbf{Remark.} Proposition~\ref{prop:dispersion} isolates the
mechanism through which polarization enters the model. The key condition is
a \emph{mean-preserving spread} of priors: polarization shifts the two groups
farther apart while leaving the population-average prior $\bar{\pi}$ unchanged.
This rules out the alternative that polarization merely correlates with
aggregate pessimism or optimism about firm quality. Under this condition, the
posterior variance increases strictly --- more polarized priors generate more
dispersed beliefs after observing the same signal. The proposition thereby provides the formal microfoundation for the primary
empirical prediction: more dispersed posteriors produce higher
disagreement-driven trading volume (Prediction~1). Larger absolute price
movements (Prediction~2) follow from the same dispersion mechanism under
additional market-friction assumptions but are not formally derived here.
The result is stated for a tractable two-group setting; extension to
richer prior distributions would require additional assumptions on the
shape of the distribution and is left for future work.

\subsection{Equilibrium Prices and Trading}

Trading volume is increasing in posterior belief dispersion
\citep{harris1993, kandel1995}:
\begin{equation}
    \label{eq:volume}
    \frac{\partial\, V}{\partial\, \mathrm{Var}[\phi(\pi_g)]} > 0.
\end{equation}

By Proposition~\ref{prop:dispersion}, polarization strictly increases
posterior belief dispersion. Trading volume is the outcome most directly
linked to this result: more dispersed posteriors generate more investor
pairs with divergent beliefs and hence mutually beneficial trading
opportunities, raising aggregate volume even in the absence of private
information.

\paragraph{From posterior dispersion to absolute returns.}
The mapping from posterior-belief dispersion to trading volume is direct:
when investors form more dispersed posteriors after the same public signal,
more pairs of investors have opposing desired trades, increasing turnover.
The link to absolute abnormal returns requires one additional
market-clearing ingredient. Suppose investor $i$ demands
\[
    q_i(P) = \alpha_i\bigl(\mu_i - P\bigr),
\]
where $\mu_i$ is investor $i$'s posterior valuation and $\alpha_i > 0$
captures risk-bearing capacity. If pessimistic investors can short without
friction and all trades clear symmetrically, disagreement need not generate
large price movements even though it increases volume. By contrast, under
standard limits to arbitrage --- such as short-sale constraints,
heterogeneous risk-bearing capacity, or segmented participation
\citep{miller1977, hong2003, gromb2010} --- optimistic and pessimistic
demands do not offset one-for-one. In that case, greater posterior
dispersion generates larger net order imbalances and therefore larger
equilibrium price adjustments in absolute value. We therefore view $AbVol$
as the sharpest implication of the model, and $|CAR|$ as a secondary
outcome that follows under empirically plausible market-friction
assumptions.

\subsection{Role of Signal Ambiguity}
\label{sec:ambiguity}

The model predicts that polarization effects are larger when audit signals
are more ambiguous. The mechanism runs not through the objective
log-likelihood ratio $\ell$ itself, but through the \emph{dispersion of
perceived precision} $|\kappa_D - \kappa_R|$ that ambiguity induces.

In the unified framework of Proposition~\ref{prop:unified}, each group's
posterior log-odds is $X_g = a(\pi_g) + \tau_g \kappa_g \ell$, where
$\ell = \log(p_H/p_L)$ is the objective log-likelihood ratio and $\tau_g$,
$\kappa_g$ capture group $g$'s trust in and perceived precision of the
disclosure. The cross-group gap is
$|X_D - X_R| = |a(\pi_D) - a(\pi_R) + (\tau_D \kappa_D - \tau_R \kappa_R)\ell|$.
When a filing provides clear, objective guidance about the nature of the
auditor change (e.g., a disclosed disagreement or a transparent quality
transition), investors face less uncertainty about the signal's
informativeness; their perceived precisions converge ($\kappa_D \approx
\kappa_R$), and the subjective term $(\tau_D \kappa_D - \tau_R \kappa_R)\ell$
contributes little to the cross-group gap regardless of $\ell$. When the
filing is ambiguous --- providing limited objective guidance about fault or
severity --- investors must form their own assessments of how informative the
disclosure is, and these assessments diverge along politically shaped lines:
$|\kappa_D - \kappa_R|$ widens, amplifying the subjective contribution to
$|X_D - X_R|$ and thereby increasing posterior variance
(Proposition~\ref{prop:precision}). Ambiguous signals therefore \emph{widen
the dispersion of perceived precision} across politically heterogeneous
investors --- precisely where political identity shapes belief formation.

In our setting, signal ambiguity varies systematically across auditor-change
events. We define signal ambiguity as the degree of interpretive latitude left
by the filing regarding the severity, source, or implications of the auditor
change. An auditor departure following a disclosed disagreement over accounting
estimates or a qualified opinion leaves investors with less interpretive
latitude: the filing itself provides guidance about fault and severity.
A Big-4-to-Big-4 lateral move with a generic or absent stated reason provides
little objective information; investors must rely more heavily on their
subjective assessment of what the change portends, a judgment shaped by their
trust in auditors and the PCAOB as institutions.

Empirically, however, ambiguity and economic materiality are difficult to
separate in this setting. Events we classify as high-ambiguity --- lateral
moves without disclosed disagreements --- tend also to be less economically
consequential: the absence of a quality-tier transition or a formal
disagreement suggests that less is at stake. Events classified as
low-ambiguity --- those involving quality-tier transitions or disclosed
disagreements --- carry clearer signals but also signal that something
material has occurred. The model's prediction holds interpretive latitude
constant while varying materiality, but our observable indicator captures
both dimensions simultaneously.

We construct a \texttt{high\_ambiguity} indicator from observable filing
characteristics (defined formally in Section~\ref{sec:design}) and interact
it with the polarization measure in P3 below.

\subsection{Testable Predictions}

\begin{itemize}
    \item[\textbf{P1.}] \textit{Polarization and trading volume (primary formal
    prediction).} By Proposition~\ref{prop:dispersion} and
    Equation~\eqref{eq:volume}, polarization increases posterior-belief
    variance, which increases disagreement-driven trading volume. This is
    the primary formal implication of the model. We test P1 using abnormal
    trading volume ($AbVol$) as the outcome (defined in
    Section~\ref{sec:design}).

    \item[\textbf{P2.}] \textit{Polarization and absolute returns (secondary
    empirical prediction).} When investors on opposing sides of the prior
    distribution revise beliefs in opposite directions, absolute price
    movements are amplified even when the average signed reaction is close to
    zero. This prediction is consistent with the model's dispersion mechanism,
    but the link from posterior variance to $|CAR|$ depends additionally on
    demand asymmetry, short-sale constraints, or limits to arbitrage
    \citep{miller1977, hong2003, gromb2010}. We therefore treat $|CAR|$
    as a complementary empirical outcome: evidence that polarization increases
    both $AbVol$ and $|CAR|$ is more informative than either alone, but $AbVol$
    is the cleaner formal prediction. We test P2 by regressing $|CAR[-1,+1]|$
    on the state-year polarization measure, with the same controls and fixed
    effects as P1.

    \item[\textbf{P3.}] \textit{Ambiguity amplification.} Per
    Section~\ref{sec:ambiguity}, ambiguous filings induce greater dispersion
    in perceived signal precision ($|\kappa_D - \kappa_R|$), because
    investors must form their own assessments of how informative the
    disclosure is. This wider dispersion amplifies the subjective
    contribution to the cross-group gap in posterior log-odds
    (Proposition~\ref{prop:precision}). Holding economic materiality
    constant, polarization effects should therefore be larger for more
    ambiguous events. We operationalize this as an interaction between
    the polarization measure and a \texttt{high\_ambiguity} indicator
    constructed from observable filing characteristics. A positive
    interaction coefficient, above and beyond any polarization main
    effect, would support the interpretation channel. However, as
    discussed in Section~\ref{sec:ambiguity}, our indicator conflates
    interpretive latitude with economic significance --- high-ambiguity
    events tend also to be less consequential --- so the test has lower
    power than an ideal experiment that varies ambiguity independently
    of materiality. We complement this test with the event-type split
    (P1--P2 by dismissal vs.\ non-dismissal), which holds materiality
    more constant: both event types involve a consequential auditor
    departure, but non-dismissals provide less filing-level guidance
    about the cause of the separation.
\end{itemize}

\textbf{Discussion.} The model formalizes one specific channel --- heterogeneous
priors --- but the same comparative statics arise under the other two channels
described in Section~\ref{sec:ambiguity}: heterogeneous institutional trust and
heterogeneous perceived signal precision. Both are nested in the unified
log-odds framework of Section~\ref{sec:ambiguity}. Whenever polarization
widens the cross-group gap $|X_D - X_R|$ --- whether through divergent priors,
divergent trust, or divergent perceived precision --- the logistic (sigmoid)
function $\sigma(x) = 1/(1+e^{-x})$ is strictly increasing, so the group-level
posterior means $\mu_g \equiv \sigma(X_g)$ satisfy $|\mu_D - \mu_R|$ increases
strictly. It follows that
posterior variance $\omega_D \omega_R (\mu_D - \mu_R)^2$ increases under any channel
(see Appendix~\ref{app:proofs} for formal statements and proofs). The core prediction is therefore
channel-agnostic: polarization amplifies belief-dispersion-driven trading and
price outcomes regardless of which specific mechanism predominates. The ambiguity
interaction in P3 operates through a complementary mechanism: ambiguous
filings widen the cross-group gap in perceived signal precision
$|\kappa_D - \kappa_R|$, amplifying the subjective contribution to
posterior dispersion even when the objective likelihood ratio $\ell$ is held
fixed. A further implication is that standard disclosure-based remedies
cannot fully eliminate polarization-driven disagreement, because the
heterogeneity lies in how investors process signals, not in what the signals
contain.

% ── 4. Hypothesis Development ─────────────────────────────────────────────────

\section{Hypothesis Development}
\label{sec:hypotheses}

\begin{hyp}
    \label{h1}
    Investor reactions to auditor-change disclosures are larger in magnitude
    in more politically polarized environments. Specifically, abnormal
    trading volume ($AbVol$) around auditor-change events is increasing in
    political polarization (primary formal prediction, per
    Proposition~\ref{prop:dispersion}), and absolute cumulative abnormal
    returns ($|CAR[-1,+1]|$) are increasing in polarization as a secondary
    empirical prediction.
\end{hyp}

\noindent\textbf{Exploratory Prediction (Event Type).}
The formal model does not parameterize event type, so this prediction is not
derived from the theoretical framework. We nonetheless examine whether the
polarization effect differs between auditor resignations and client-initiated
dismissals, motivated by the ambiguity logic of Section~\ref{sec:ambiguity}.
Although the prior literature characterizes resignations as worse-news signals
on average \citep{ghosh2015, beneish2005}, the relevant distinction for our
purposes is \emph{per-filing} informational content. SEC rules require
registrants to disclose specified disagreements and reportable events, but
professional standards restrict the predecessor auditor from disclosing
confidential client information without consent. Consequently,
\citet{beneish2005} document that approximately three-quarters of resignation
8-Ks carry no attribution to any accounting disagreement, and
\citet{boone2001} find that the resignation announcement does not reduce
information asymmetry --- investors must draw their own inferences,
relying on priors about auditor credibility rather than on the filing's
content. Dismissals, in contrast, assign initiative to the client,
providing directional information about the nature of the separation even
when the stated reason is sparse.
We treat this as an auxiliary empirical exercise (Table~\ref{tab:event_type})
rather than a core hypothesis.

\begin{hyp}
    \label{h2}
    The polarization effect on post-event investor uncertainty is
    stronger when the Item~4.01 filing is less informative about the
    circumstances of the auditor change. We operationalize filing
    informativeness with a text-based measure --- a filing specificity
    index and a boilerplate-adjusted nonstandard word count,
    residualized on materiality correlates --- that isolates interpretive
    latitude from the economic materiality of the underlying event. Per
    Section~\ref{sec:ambiguity}, when the filing provides less objective
    content, investors rely more heavily on their subjective priors
    about audit credibility, and polarization amplifies the dispersion
    of those priors. This is the primary cross-sectional test of the
    interpretation channel.
\end{hyp}

% ── 5. Empirical Design ───────────────────────────────────────────────────────

\section{Empirical Design}
\label{sec:design}

\subsection{Sample Construction}

\textbf{Auditor change events.} We identify auditor changes using Form~8-K
filings disclosing a change in the registrant's certifying accountant (Item
4.01), obtained from SEC EDGAR for 2001--2023.\footnote{We end the sample in
2023, the last full year for which DW-NOMINATE ideological scores are
available in final form from Voteview. Scores for the 119th Congress (which
began January 2025) have not yet been finalized at the time of writing. The
Esteban-Ray electoral measure covers the same period, as MIT Election Lab
House returns are available through the 2022 midterm election, which is
forward-filled to cover calendar years through 2023.} We retain only
original 8-K filings (excluding 1,720 amendments) matched to a CRSP PERMNO
and require at least 100 non-missing trading days in the estimation window.
Table~\ref{tab:attrition} reports the full attrition. Of 6,901 original
filings, 5,628 cannot be linked to a CRSP/Compustat security --- primarily
because the filers are micro-cap or OTC registrants not covered by
CRSP.\footnote{Panel B of Table~\ref{tab:attrition} compares observable
characteristics of matched and unmatched filings. Disagreement rates are
broadly similar (67\% vs.\ 60\%); the primary difference is firm size,
proxied by Big~4 auditor involvement (43\% vs.\ 14\%). The matched sample
is therefore tilted toward larger, exchange-listed firms --- a standard
feature of CRSP/Compustat-based research designs in the auditing literature
\citep{defond2014}. Because our theory operates through investor belief
heterogeneity rather than firm size per se, this selection is conservative:
to the extent that larger firms have more dispersed and sophisticated
investor bases, the local-investor channel should be \emph{weaker}, not
stronger, in the matched sample.} The final sample consists
of 678 auditor-change events for 456 unique firms after excluding financial
firms (SIC 6000--6999), utilities (SIC 4900--4999), and events with missing
Compustat controls or headquarters-state
information.\footnote{Of the 1,220 CRSP-matched events, 536 are dropped
for missing Compustat controls or headquarters-state information
(primarily firms with no Compustat financial records despite possessing a
CRSP--Compustat link key), and 6 are dropped by the financial and utility
industry screens (SIC 4900--4999, 6000--6999). The attrition is therefore
driven almost entirely by data availability, not researcher discretion.}

\input{../Output/Tables/tab_sample_attrition}

\subsection{Dependent Variables}

\textbf{Abnormal trading volume ($AbVol$).} We measure trading-volume
reactions over the $[-1, +1]$ event window, consistent with the short-run
agreement-to-disagree framework of \citet{kandel1995} in which volume spikes
at the moment beliefs diverge. $AbVol_e$ is the mean of
$[\log(\mathrm{Vol}_{e,t}+1) - \overline{\log(\mathrm{Vol}_e)}]$ over the
$[-1,+1]$ window, where the baseline is the estimation-window mean.

\textbf{Absolute cumulative abnormal return ($|CAR|$).} Following standard
event-study methodology \citep{mackinlay1997}, we estimate a market model
over the estimation window $[-252, -46]$ trading days relative to the event
date, using at least 100 non-missing trading days to estimate parameters:
\begin{equation}
    AR_{e,t} = R_{e,t} - (\hat{\alpha}_e + \hat{\beta}_e \cdot R_{m,t}),
    \quad t \in \{-1, 0, +1\}.
\end{equation}
The window begins 252 days before the event to capture a full trading year
of pre-event returns and ends 46 days before to avoid contamination from
information leakage in the run-up period. $CAR_e[-1,+1] = \sum_{t=-1}^{+1} AR_{e,t}$
and $|CAR_e[-1,+1]|$ is a secondary dependent variable. We use the CRSP
value-weighted return as the market return and include delisting returns
following \citet{beaver2007}.

\subsection{Political Polarization Measure}

A central empirical challenge is that the theory's polarization object ---
the latent force that increases divergence in interpretation through identity,
alienation, and perceived institutional credibility --- is not directly
observable at the investor level \citep{duclos2004}. The available data
provide only grouped or indirect proxies, each of which captures a different
margin of the latent concept \citep{esteban1994, esteban2007}. We therefore examine three
complementary proxies rather than treating any single measure as definitive.
The state-level presidential polarization measure below captures
\emph{cross-sectional partisan division}; DW-NOMINATE captures
\emph{elite ideological distance}; and the within-state county vote-share
standard deviation captures \emph{geographic partisan sorting}. These measure different aspects of the
political landscape \citep{wang2000}.\footnote{%
The continuous-density estimators developed by \citet{duclos2004} provide
the most rigorous formalization of the identity--alienation concept, but
require a directly observed distribution of the underlying investor-level
trait. Because our setting does not yield a firm-year density of investor
political identity, we use reduced-form political-environment proxies instead.}

We measure state-level partisan polarization from county-level presidential
election returns (MIT Election Lab, 2000--2020). For state $s$ and presidential
election year $t^{*}$, let $D_{s,t^{*}}$ and $R_{s,t^{*}} = 1 - D_{s,t^{*}}$ denote the
Democratic and Republican two-party vote shares aggregated across counties.
The partisan margin is $M_{s,t^{*}} = |D_{s,t^{*}} - R_{s,t^{*}}|$, ranging from zero in
perfectly contested states to one in completely one-sided states. We define
\emph{partisan polarization} as:
\begin{equation}
    \label{eq:comp}
    \text{Polarization}_{s,t^{*}} = 1 - M_{s,t^{*}} = 1 - |D_{s,t^{*}} - R_{s,t^{*}}|,
\end{equation}
which is maximized at 1.0 when both parties split the vote equally and
minimized at 0 in one-party states. Higher values indicate a more evenly
divided electorate, which we interpret as reflecting greater partisan
polarization in the investor base. More polarized
states are politically divided environments where investors are more
likely to hold heterogeneous priors
about institutional trustworthiness and the interpretation of regulatory
signals.\footnote{We also test the Esteban-Ray polarization index
$P^{ER}_{s,t^{*}} = D_{s,t^{*}} \cdot R_{s,t^{*}}$, computed at the state level from the
same presidential returns. The ER index is concave in vote shares and
has lower discriminating power away from the 50-50 split (SD in our sample:
0.027 for the ER index vs.\ 0.101 for the margin). We therefore prefer the
linear polarization measure as the primary proxy and retain the presidential
ER index as a robustness check (Table~\ref{tab:robustness}, column 2). The
congressional-district ER index based on U.S. House returns is also tested in
column 3 of Table~\ref{tab:robustness}; its standard deviation is only 0.011 ---
one-ninth of the presidential margin --- reflecting gerrymandering and the
compression of competitive outcomes at the district level. \citet{mehlhaff2024group}
shows that the ER index at $\alpha=1$ is nearly indistinguishable from the
variance of the two-party vote distribution (correlation $\approx 0.93$); the
margin is a simpler and more transparent linear proxy. We prefer presidential
over congressional returns for a conceptual reason as well: a well-established
body of political-science research documents that presidential races are the
most nationalized arena of U.S. electoral competition, in the sense that
national partisan forces determine outcomes cleanly with minimal candidate- or
district-specific noise \citep{vertz1987, carson2024}. Congressional and
subnational races, by contrast, absorb additional local information and
candidate-specific variation that dilutes the national partisan signal
\citep{moskowitz2021, abramowitz2016, conevska2025}. Using presidential
returns as the basis for our polarization measure therefore better isolates
the broad, national-level partisan cleavage that we hypothesize shapes investor
belief heterogeneity.}

We forward-fill each presidential election's measure over the four subsequent
calendar years --- assigning the 2000 vote to 2001--2004, the 2004 vote to
2005--2008, and so on through the 2020 election, which covers 2021--2023
within our sample period. This assignment assumes that the state political
environment evolves at the electoral-cycle frequency rather than annually. We standardize to mean zero and unit variance
within the analysis sample. Because different polarization indices emphasize
different aspects of between-group separation and within-group cohesion, the
polarization measure cannot be treated as exhaustive \citep{wang2000}.
A complementary measure based on elite roll-call behavior is therefore needed.

As a second proxy for polarization, we construct a measure of elite ideological
distance from DW-NOMINATE first-dimension scores \citep{poole1997,poole2007}.
DW-NOMINATE scores capture legislators' revealed ideological positions from
roll-call voting records, rather than electoral outcomes, and thus measure
\emph{ideological} polarization directly. For each state $s$ and Congress $c$,
we compute:
\begin{equation}
    \label{eq:dw}
    P^{DW}_{s,c} = \overline{\text{dim1}}_{R,s,c}
    - \overline{\text{dim1}}_{D,s,c},
\end{equation}
where $\overline{\text{dim1}}_{R,s,c}$ and $\overline{\text{dim1}}_{D,s,c}$
are the mean first-dimension DW-NOMINATE scores among House Republicans and
Democrats from state $s$ in Congress $c$, respectively. Because the first
dimension captures the liberal--conservative continuum, $P^{DW}_{s,c}$ is
always positive and increasing in ideological distance between the parties.
We expand each Congress's scores to the two calendar years it covers and
standardize to mean zero and unit variance. The national-level counterpart,
$P^{DW\text{-nat}}_{c}$, computes the same gap across all House members
nationally and varies only over time, providing a pure time-series check.
The electoral polarization and DW-NOMINATE measures are complementary proxies:
electoral polarization captures division in the mass electorate, while
DW-NOMINATE captures ideological distance among elected representatives.
If both predict the same investor response, the evidence for a polarization
mechanism is substantially stronger.

As a third proxy, we construct the population-weighted within-state standard
deviation of county-level Democratic vote shares. This \emph{county vote SD}
measure captures geographic partisan sorting: a high value indicates that a
state contains both deep-red and deep-blue counties, consistent with genuine
local polarization, while a low value indicates counties that are uniformly
similar. Crucially, this measure addresses the concern, raised by
\citet{fiorina2005}, that electoral competitiveness may reflect moderate
swing voters rather than polarized blocs: a state can be 50-50 and yet
have low county-level variance if all its counties vote near 50-50.

\smallskip
\noindent\textit{Limitations of measurement.} Each proxy is subject to
known limitations. The presidential polarization measure assigns equal
weight to all counties within a state regardless of firm location, and
forward-filling assumes no within-cycle variation. The state-level DW-NOMINATE
gap may reflect party sorting rather than genuine ideological movement and
is available only at biennial frequency.

\subsection{Cross-Sectional Variables}

\textbf{Signal ambiguity.} We construct a binary \texttt{high\_ambiguity}
indicator to operationalize P3. An event is classified as high-ambiguity if the
filing discloses no formal disagreement between the registrant and the
departing auditor \emph{and} the auditor change does not involve a clear
quality-tier transition (i.e., the change is lateral --- Big-4-to-Big-4 or
non-Big-4-to-non-Big-4 --- or the quality direction is unclassified).
High-ambiguity events comprise 120 of the 678 sample observations (17.7\%).

\textbf{Event type.} We classify each event as a \emph{dismissal} (the client
terminated the auditor) or \emph{non-dismissal} (the auditor resigned, declined
to stand for re-election, or the separation is otherwise not client-initiated),
based on the language of the 8-K filing.

\subsection{Empirical Specification}

The unit of observation is an auditor-change event $e$. We estimate:
\begin{equation}
    \label{eq:main}
    Y_e = \alpha + \beta\,\textit{Pol}_{s(e),\,t(e)}
    + \gamma' Z_{e,\,t(e)-1}
    + \lambda_{t(e)} + \delta_{j(e)} + \varepsilon_e,
\end{equation}
where $Y_e$ is $AbVol_e$ or $|CAR_e[-1,+1]|$; $\textit{Pol}_{s(e),t(e)}$ is the
standardized state political polarization measure for the headquarters state
$s(e)$ of the event's firm in event year $t(e)$;
$Z_{e,t(e)-1}$ is a vector of firm controls measured in the fiscal year prior
to the event (size, leverage, ROA, book-to-market, loss indicator, and sales
growth); $\lambda_{t(e)}$ are event-year fixed effects; and $\delta_{j(e)}$ are
two-digit SIC industry fixed effects. Standard errors are clustered at the firm
level. The coefficient of interest is $\beta$.

\subsection{Identification}

As noted in the introduction, headquarters-state polarization is a
reduced-form proxy, not a direct measure of investor beliefs. The paper
identifies whether market reactions to auditor-change disclosures vary
with the surrounding partisan environment --- not whether any specific
type of investor trades more.

\subsubsection*{Why headquarters-state polarization may be informative}

The intended channel runs through the local stakeholder environment
surrounding the firm: employees, customers, local media, and --- critically
--- retail investors, who are more geographically concentrated than
institutional investors and more likely to anchor their beliefs to local
political norms. A well-established local equity bias means that retail
investors overweight geographically proximate firms in their portfolios
\citep{coval1999}, so the headquarters state's political composition
is a meaningful, if imperfect, proxy for the political composition of the
firm's marginal retail investor base. Consistent with this channel,
\citet{boone2001} find that auditor resignation announcements generate
significant abnormal trading activity among individual investors but not
among institutional investors, suggesting that it is retail investors ---
who are more geographically concentrated and more dependent on SEC-mandated
disclosure --- who respond to the informational content of the 8-K filing. For smaller and less nationally prominent firms, the
marginal trader is more likely to be a local retail investor whose
interpretation of an auditor change is shaped by the surrounding political
environment. For larger firms with globally dispersed institutional ownership,
the headquarters-state proxy is less well-matched to the actual investor base,
and the effect should be attenuated. This cross-sectional prediction provides
a validation test: we expect the polarization effect to be stronger for
smaller firms, whose marginal investors are more likely to be local.
Column~(8) of Table~\ref{tab:robustness} restricts the sample to
below-median log-asset firms and tests this directly; the AbVol coefficient
strengthens ($\beta = 0.137$, $p < 0.05$), consistent with polarization
mattering more where the marginal investor is local.
To test the retail channel directly, we construct the institutional
ownership fraction for each event from quarterly Form 13F filings. We
download 13F-HR filings from SEC EDGAR for each quarter in 2000--2023,
parse the reported holdings tables, and aggregate total institutional
shares across all filers per firm-quarter. Normalizing by CRSP shares
outstanding gives the fraction of shares held by 13F institutional
investors at the most recent quarter-end before each event (within 180
days). We obtain matches for 674 of 678 events, with a mean institutional
ownership of 52\% (median 43\%). We then interact polarization with an
above-median \emph{high retail} indicator (one minus institutional
ownership). The retail-ownership interaction is directionally positive
for both $|CAR|$ ($\beta_{\text{interaction}} = 0.006$, $p = 0.201$) and
$AbVol$ ($\beta_{\text{interaction}} = 0.051$, $p = 0.552$), consistent
with the retail channel but statistically insignificant. Combined with
the directional small-firm result, these tests weakly support the local
retail channel but do not rule out alternative interpretations.

We acknowledge the main limitation of the proxy directly: equity investors in
publicly traded firms are not confined to the headquarters state. Institutional
ownership is national, and many retail investors hold diversified portfolios
regardless of geography. Headquarters-state polarization therefore captures
the intended channel with error. We address this in five ways. First, we
include rich firm-level controls to absorb observable firm characteristics
that may correlate with both state polarization and event-window reactions.
Second, state fixed effects (Table~\ref{tab:robustness}, column~4) absorb all
time-invariant cross-state differences in investor clientele composition,
local media environments, state regulatory environments, and industry
clustering, identifying solely from within-state changes in polarization
across election cycles. Third, the DW-NOMINATE specification uses an entirely different data source
(congressional roll-call votes) and produces variation that is not driven by
the headquarters-state aggregation choice; it significantly predicts
abnormal volume ($\beta = 0.100$, $p < 0.10$), confirming that the volume
result generalizes beyond electoral proxies.
Fourth, a county-level polarization check using MIT Election Lab county
presidential returns matched to firm headquarters counties via Compustat
zip codes provides a finer-grained geographic alternative
(Table~\ref{tab:robustness}, column~7). Fifth, the within-state standard
deviation of county-level vote shares --- a direct measure of geographic
partisan sorting that distinguishes genuinely polarized states from merely
competitive ones \citep{fiorina2005} --- independently predicts $|CAR|$
(column~9, $p = 0.056$), confirming that the result is not merely an
artifact of electoral closeness.

\subsubsection*{State-level confounds and inference}

Identification rests on two sources of variation in $\textit{Pol}_{s(e),t(e)}$:
cross-state differences in the partisan environment of presidential elections,
and time-series changes in that environment across electoral cycles. Year
fixed effects absorb aggregate macroeconomic and political conditions common
to all firms. Industry fixed effects absorb sector-level differences in
auditor-change frequency and investor base composition. The key identifying
assumption is that, conditional on these controls, a firm's headquarters-state
polarization at the time of the event is uncorrelated with unobserved
determinants of the market's reaction to that specific auditor change.

Four state-level confounds deserve explicit discussion. \emph{Local investor
clientele}: politically polarized states may attract systematically different
retail-investor populations whose risk tolerance or information processing
differs for reasons unrelated to polarization per se. We address this through
state fixed effects, which absorb the time-invariant component of clientele
composition. \emph{Local media ecosystems}: more polarized states may have
more polarized local media that amplifies any corporate news event, not just
auditor changes. If so, the polarization effect should appear equally for
non-audit events; the ambiguity heterogeneity results (Table~\ref{tab:ambiguity})
partially address this by showing the effect is concentrated in events with
audit-specific informational content. \emph{State business and regulatory environments}: states with
more polarized electorates may also have different securities litigation
climates or governance norms that independently affect how auditor changes
are processed. State fixed effects absorb time-invariant components; the
time-varying component is plausibly orthogonal to specific auditor-change
timing within the state. \emph{Industry clustering}: some high-polarization
states (e.g., Texas for energy, California for technology) have distinctive
industry concentrations. Two-digit SIC industry fixed effects absorb this
directly.

Because the polarization regressor varies at the state$\times$year level,
columns~(5) and~(6) of Table~\ref{tab:robustness} address this concern:
column~(5) clusters at the state level and column~(6) implements two-way
clustering by firm and state following \citet{cameron2011}; the baseline
clusters at the firm level, which is conservative for event-level inference
but potentially optimistic relative to the regressor's level of variation.

% ── 6. Results ────────────────────────────────────────────────────────────────

\section{Results}
\label{sec:results}

\subsection{Descriptive Statistics}

Table~\ref{tab:summary} presents descriptive statistics for the 678 auditor-change
events in the estimation sample. Abnormal trading volume averages 0.11 units above
the estimation-window baseline, indicating that auditor-change events generate
measurable abnormal trading activity. The mean $|CAR[-1,+1]|$ is 5.0\% with a
standard deviation of 6.7\%, consistent with prior event studies of auditor changes
\citep{defond2014}. The mean partisan margin ($|D-R|$, the complement of the primary polarization
measure) is 0.13 (SD 0.10), spanning from near-zero for highly contested
states to 0.40 for strongly one-party states; equivalently, mean partisan
polarization is 0.87. The median firm has log assets of 4.97 and leverage
of 17\%; 45\% report a loss in the year preceding the auditor change, reflecting
the high loss incidence in this sample.

\input{../Output/Tables/tab01_summary_stats}

\subsection{Main Results}

Table~\ref{tab:main} reports the baseline results. Columns (1)--(2) use
abnormal volume as the dependent variable (the primary formal prediction);
columns (3)--(4) use $|CAR[-1,+1]|$. Odd columns include year fixed effects
only; even columns add industry fixed effects and the full set of firm
controls. Across all four specifications, the coefficient on
\textit{Polarization} is positive and statistically significant, ranging
from $\beta = 0.119$ ($p = 0.006$) to $\beta = 0.111$ ($p = 0.010$) for
abnormal volume, and from $\beta = 0.006$ ($p = 0.015$) to
$\beta = 0.005$ ($p = 0.039$) for $|CAR|$.
The economic magnitude is meaningful: a one-standard-deviation increase in partisan
polarization is associated with a 0.11-unit increase in abnormal volume
and a 0.5 percentage point increase in $|CAR|$ relative to a sample mean of 5.0\%.
Notably, the volume result is stronger and more precisely estimated ($p = 0.010$)
than the absolute return result ($p = 0.039$). This ordering is predicted by
disagreement models \citep{kandel1995}: when investors receive the same signal
but form heterogeneous posteriors, the most direct consequence is increased
trading as optimists buy from pessimists; the effect on unsigned returns is a
secondary implication that depends on the relative wealth and aggressiveness of
disagreeing investor groups. The fact that the volume channel is more robust
than the price channel --- a pattern that extends to alternative
polarization proxies in Table~\ref{tab:robustness} --- is consistent with
the disagreement mechanism rather than generic salience, which would
predict at least as strong a price effect as a volume effect.

\input{../Output/Tables/tab02_main_results}

\subsection{Filing Informativeness and Post-Event Uncertainty}
\label{sec:informativeness}

The interpretation channel predicts that polarization effects should be
larger for filings that provide less objective guidance, because investors
with divergent priors have less objective anchor text to ground their
interpretation. Testing this prediction requires a measure of filing
informativeness that varies within the setting without being confounded
with economic materiality. Our initial indicator --- \texttt{high\_ambiguity}
(no disclosed disagreement plus a lateral quality-tier transition) ---
fails this requirement: lateral Big-4-to-Big-4 switches are both less
interpretively informative and less economically material, so the measure
cannot separate the two effects. Results using that indicator do not
produce the predicted monotonic pattern.\footnote{Using the binary
\texttt{high\_ambiguity} indicator, the low-ambiguity subsample drives
the volume result ($\beta = 0.114$, $p = 0.008$) while the
high-ambiguity subsample is insignificant ($p = 0.422$). The $|CAR|$
pattern is directionally consistent with P3 but underpowered at
$N = 120$. These results are available upon request.}

We therefore construct two cleaner measures of filing informativeness
that operate within the text of the filing itself, orthogonal to
observable event features. First, we build a \emph{filing specificity
index} that aggregates seven binary indicators identified from the text
of the Item~4.01 section: whether the filing states an explicit cause of
the change, names a concrete accounting or audit issue, identifies a
specific domain of disagreement, describes a reportable event beyond the
standard disclaimer, provides audit committee process detail beyond
generic language, links the change to another corporate transaction, or
contains non-generic causal language beyond statutory compliance
phrasing. Second, we build a \emph{boilerplate-adjusted nonstandard word
count}: we strip the standard Regulation S-K Item~304 disclaimer
sentences from each filing and count the remaining words, then
residualize the log of this count on dismissal, firm size, and year
fixed effects to remove variation correlated with economic materiality.
A binary \emph{Low Info} indicator equals one for filings in the bottom
tercile of the residualized measure. The two measures capture different
aspects of informativeness but give similar ordinal rankings of the
sample.

\smallskip
\noindent\textit{Validation via post-event uncertainty.}
We validate the Low Info measure against six independent post-event
uncertainty proxies, computed over trading days $[+2, +20]$ relative to
the filing date: (i) the standard deviation of abnormal daily returns,
(ii) the \citet{parkinson1980} high-low volatility estimator, (iii) the
\citet{amihud2002} illiquidity ratio, (iv) the relative bid-ask spread,
(v) abnormal volume persistence, and (vi) the \citet{roll1984} implied
spread. For each measure, we compute the change from pre-event
$[-20, -2]$ to post-event $[+2, +20]$ and regress it on the Low Info
indicator, controlling for the pre-event level, firm characteristics,
and year/industry fixed effects. Five of the six coefficients on
Low Info are positive (theory-consistent); the sixth (volume
persistence) is directionally ambiguous because the full volume reaction
is absorbed by the pre-event control. No individual validation test is
significant at $N \approx 720$, but the directional consistency is
meaningful given that the six measures are only modestly correlated
(mean pairwise $r = 0.22$).

\smallskip
\noindent\textit{Mechanism test: polarization $\times$ Low Info.}
Table~\ref{tab:ambiguity} reports the mechanism test: does the
polarization effect on each post-event uncertainty measure amplify when
filings are less informative? The interpretation channel predicts a
positive coefficient on \textit{Polarization} $\times$ \textit{Low Info}
for every measure.
The results are directionally consistent with the proposed mechanism: the
Polarization $\times$ Low Info interaction is positive for
\emph{all six measures}. Individual interactions are not significant
(smallest $p = 0.163$ for Parkinson high-low volatility), reflecting
limited power at $N \approx 720$ per specification. However, a one-sided
binomial test on sign consistency --- with theory pre-specifying the
positive direction --- yields $p = 0.016$: under a null of no mechanism,
the probability of observing all six coefficients positive is
$1/64 \approx 1.6\%$.
A continuous composite uncertainty index, constructed as the
equal-weighted average of the six standardized measures, produces the
same directional result: the coefficient on \textit{Polarization}
$\times$ (continuous nonstandard word count) is $-0.064$
($p = 0.124$)---negative, meaning the polarization effect attenuates as
filings become more informative, consistent with the mechanism but
marginal at conventional significance.

We interpret this pattern as directionally supportive but not
dispositive evidence for the interpretation channel. Individual
mechanism tests are underpowered; the joint sign consistency provides
suggestive evidence consistent with the proposed mechanism,
while the failure of any single measure to reach significance reflects
the difficulty of identifying the mechanism with reduced-form
cross-sectional variation at our sample size.

\input{../Output/Tables/tab04_ambiguity}

\subsection{Exploratory Heterogeneity by Event Type}

Table~\ref{tab:event_type} splits the sample by event type. The
event-type heterogeneity yields a mixed pattern across the two outcomes.
For $|CAR|$ (columns 3--4), the effect is concentrated in non-dismissal
events (primarily auditor resignations): $\beta = 0.011$, $p = 0.043$.
Among dismissals, the coefficient is statistically indistinguishable from
zero ($\beta = 0.003$, $p = 0.189$). For abnormal volume (columns 1--2),
the pattern reverses: polarization significantly predicts volume for
dismissals ($\beta = 0.134$, $p = 0.006$) but not for non-dismissals
($\beta = 0.122$, $p = 0.164$).

We do not view these splits as decisive evidence on the interpretation
channel given the inconsistency across outcomes. One possible
interpretation is that dismissals, while more transparent in their
adversarial nature, still generate substantial disagreement about the
\emph{consequences} of the change --- particularly whether the firm's
audit quality will suffer --- and this disagreement manifests in trading
volume rather than unsigned price movement. Non-dismissals, where the
filing typically provides less explicit attribution
\citep{beneish2005, boone2001}, show the stronger $|CAR|$ result,
consistent with polarization effects on prices being amplified when
investors must rely more on their own priors. We treat these event-type
splits as descriptive rather than as decisive mechanism evidence; the
primary specificity argument rests on the earnings-announcement placebo
(Section~\ref{sec:placebo}).

\input{../Output/Tables/tab03_event_type}

\subsection{Robustness and Alternative Proxies}

Table~\ref{tab:robustness} addresses conventional robustness concerns and
examines whether the baseline result extends to alternative polarization
proxies. Panel~A reports results for abnormal volume (the primary formal
prediction); Panel~B reports $|CAR|$. All column numbers refer to the
same specification across both panels.

\textbf{Alternative proxies.}
Column~(1) repeats the baseline. Column~(2) substitutes the quadratic
presidential Esteban-Ray index for the linear polarization measure.
For AbVol, the coefficient remains significant ($\beta = 0.081$, $p < 0.05$);
for $|CAR|$, it is directionally consistent but attenuated
($\beta = 0.003$, $p = 0.124$), reflecting the lower discriminating power
of the quadratic form in less-divided states. Column~(3) replaces the
electoral measure with the DW-NOMINATE state-level cross-party ideological
gap, which captures elite ideological distance rather than electoral
division. This proxy is significant for abnormal volume
($\beta = 0.100$, $p < 0.10$) but not for $|CAR|$
($\beta = 0.002$, $p = 0.522$). The divergence across outcomes is
informative: elite ideological distance moves trading volume --- the
direct disagreement prediction --- even though it does not generate the
additional price effects that require demand asymmetries. The $|CAR|$
null for DW-NOMINATE is therefore consistent with the theoretical
hierarchy in which volume is the sharper prediction and absolute returns
follow only under additional market-friction conditions.\footnote{Pairwise
correlations among the standardized proxies confirm that they capture
distinct dimensions of the latent polarization concept: electoral
polarization and the presidential ER index are highly correlated ($r = 0.87$), but
both are weakly correlated with DW-NOMINATE ($r = 0.10$ and $0.16$,
respectively), county-level polarization ($r = 0.45$ and $0.43$),
and county vote SD ($r = 0.08$ and $0.11$). County vote SD and
DW-NOMINATE share moderate correlation ($r = 0.29$), consistent with
geographic sorting and elite polarization capturing related but distinct
phenomena.}

\textbf{Specification robustness.}
Column~(4) augments the baseline with state fixed effects. The AbVol
coefficient is directionally positive but loses precision
($\beta = 0.066$, $p > 0.10$); the $|CAR|$ coefficient is similar
($\beta = 0.012$, $p = 0.144$). Both nulls are consistent with
within-state temporal variation in partisan polarization being noisier
than cross-state variation: of the 124 state$\times$election-cycle cells
that contain auditor-change events, 52 contain only a single event,
limiting the power of a within-state design. Our identification
therefore relies primarily on cross-state differences in the partisan
environment rather than within-state changes over time.
Columns~(5)--(6) test alternative clustering structures. State-level
clustering (column~5) and two-way clustering by firm and state following
\citet{cameron2011} (column~6) leave both outcomes unchanged and
significant: AbVol at $p < 0.001$ in both cases, $|CAR|$ at $p = 0.028$
under state clustering,
confirming that the baseline inference is not driven by the choice of
clustering level.

\textbf{Geographic scale.}
Column~(7) replaces the state-level measure with a county-level analogue
constructed from the same MIT Election Lab presidential returns, matched
to each firm's headquarters county via Compustat zip codes and the HUD
ZIP-COUNTY crosswalk. For $|CAR|$, the coefficient is $\beta = 0.005$
($p = 0.036$, $N = 659$), virtually identical to the state-level
baseline, confirming that the result is not an artifact of geographic
aggregation. For AbVol, the county-level coefficient is near zero
($\beta = 0.022$, $p > 0.10$). The divergence across dependent variables
is theoretically informative. Prices are set by marginal investors, and
the local bias literature documents that geographically proximate
investors are disproportionately represented among a firm's shareholders
and are more likely to be marginal price-setters
\citep{coval1999}. County-level partisanship therefore
captures the political environment of the investors whose trades move
prices, explaining the significant $|CAR|$ result. Trading volume, by
contrast, requires participants on both sides of the trade and thus
reflects belief dispersion across the \emph{full} investor base, which
is geographically dispersed well beyond the headquarters county. A single
county's partisan lean is too narrow to proxy for this cross-investor
heterogeneity; the state-level measure better captures the political
environment that shapes the broader set of investors who generate
disagreement-driven trade. A horse-race specification including both state
and county competitiveness simultaneously (Table~\ref{tab:supplementary},
columns~1--2) confirms that state-level variation dominates for AbVol
($\beta_{\text{state}} = 0.125$, $p = 0.012$;
$\beta_{\text{county}} = -0.030$, $p = 0.535$), while neither measure
dominates for $|CAR|$, where both capture overlapping variation in the
marginal investor's political environment.

\textbf{Small-firm subsample.}
Column~(8) restricts the sample to below-median log-asset firms ($N = 339$).
The AbVol coefficient strengthens ($\beta = 0.137$, $p < 0.05$), consistent
with the local-investor channel: smaller firms have more geographically
concentrated retail investor bases, so headquarters-state polarization is
a better-matched proxy. The $|CAR|$ coefficient is directionally
consistent ($\beta = 0.005$, $p = 0.175$) but imprecise given the smaller
subsample.

\textbf{Electoral polarization versus swing voters.}
A natural concern is that electoral polarization captures moderate swing
voters rather than genuinely polarized blocs \citep{fiorina2005}. A 50-50
state could be evenly split because its voters are centrists who swing
between parties, not because it contains ideologically opposed camps. To
address this distinction, column~(9) replaces the baseline measure with the
population-weighted within-state standard deviation of county-level
Democratic vote shares. This measure captures \emph{geographic partisan
sorting}: a high value indicates a state with both deep-red and deep-blue
counties --- genuine local polarization --- while a low value indicates
counties that are uniformly similar regardless of the statewide margin.
For $|CAR|$, the coefficient is $\beta = 0.005$ ($p = 0.056$), marginally
significant and similar in magnitude to the baseline. For AbVol, the
coefficient is directionally positive ($\beta = 0.066$, $p > 0.10$) but
does not reach significance.
Column~(10) includes both the baseline polarization measure and the
county vote-share SD jointly, along with their interaction; the interaction
is insignificant in both panels ($p > 0.30$), indicating that the two
proxies capture overlapping variation rather than a conditional effect.

\textbf{Summary.} Across both panels, the pattern is consistent with the
theoretical hierarchy: abnormal volume --- the direct disagreement
prediction --- is robust to three conceptually distinct polarization
proxies (electoral polarization, ER index, and DW-NOMINATE), alternative
clustering structures, and the small-firm subsample restriction. Absolute
returns are more fragile across alternative proxies, as expected given that
the link from posterior dispersion to $|CAR|$ depends on additional
market-friction conditions. The proxies that are null for $|CAR|$ (ER
index, DW-NOMINATE) are significant for AbVol, indicating that the absence
of a price effect does not imply the absence of disagreement.

To address concerns about finite-sample inference with $N = 678$, we implement
a permutation (randomization) test for both baseline coefficients. We reshuffle
the \textit{Polarization} variable across observations 5,000 times, holding
all other variables fixed, and re-estimate $\beta$ each time. For AbVol, the
actual coefficient falls at the 99.6th percentile of the null distribution,
yielding a one-sided permutation $p$-value of 0.004. For $|CAR|$, the
permutation $p$-value is 0.029. Both confirm that the baseline results are
not artifacts of finite-sample distributional assumptions.
More broadly, the fact that we detect effects at conventional significance
levels despite the moderate sample size implies that the underlying effect
sizes are economically large --- a point reinforced by the subsample tests,
where splits that reduce $N$ substantially still produce significant
coefficients (e.g., Table~\ref{tab:event_type}, dismissal AbVol with
$N = 421$, $p < 0.01$; Table~\ref{tab:event_type}, non-dismissal $|CAR|$
with $N = 257$, $p < 0.05$).
Table~\ref{tab:permutation} reports the full permutation test results.

\textbf{Regulatory regime stability.}
The sample spans several changes to the audit disclosure environment, most
notably the Sarbanes-Oxley Act of 2002 --- which created the PCAOB --- and
the SEC's 2004 overhaul of Form~8-K (Release No.~33-8400), which
accelerated filing deadlines to four business days. Although the 2004
reform expanded Form~8-K generally, the SEC stated that Item~4.01 was
``substantively the same as former Item~4,'' with only limited textual
reorganization; the substantive content requirements governing
auditor-change disclosures were not materially altered. To test whether the
polarization effect depends on the post-SOX institutional regime, we
interact the polarization measure with an indicator for events occurring in
2003 or later (Table~\ref{tab:supplementary}, columns~3--4). The interaction is
insignificant for both $|CAR|$ ($p = 0.498$) and $AbVol$ ($p = 0.970$),
and the polarization coefficient is directionally positive in both the
pre-SOX and post-SOX subsamples (Table~\ref{tab:supplementary}, columns~5--8).
The effect does not depend on the PCAOB's existence, consistent with the
mechanism operating through institutional trust broadly rather than through
any single institution.\footnote{The PCAOB's
AS~3101, which introduced critical audit matter (CAM) disclosures effective
2019--2020, represents a further change to the audit information
environment. Only 40 sample events occur after 2019, precluding a
well-powered test. Whether CAM disclosures attenuate polarization-driven
disagreement by providing richer audit-specific information is an important
question for future research as the post-CAM sample grows.}

\input{../Output/Tables/tab05_robustness}

\input{../Output/Tables/tab07_permutation}

\textbf{Ideological versus affective polarization.}
The political science literature distinguishes ideological polarization
from affective polarization (out-party animus; \citealp{iyengar2012,
iyengar2019}). To test whether the baseline result reflects the latter,
we augment the specification with the ANES feeling-thermometer partisan
differential interacted with state-level partisan exposure (Appendix
Table~\ref{tab:affective}). The affective interaction is null for both
outcomes ($p > 0.10$), while the ideological polarization coefficient is
unchanged. This is consistent with the mechanism operating through the
cross-sectional partisan composition of the local electorate rather than
through time-varying partisan animus, though we note that the ANES series
is coarse and a state- or investor-level affective measure could yield
different conclusions.

\subsection{Placebo Test: Earnings Announcements}
\label{sec:placebo}

A natural concern is that headquarters-state polarization simply amplifies
market reactions to any corporate news event, not specifically to disclosures
that require interpretation. We address this with a within-firm placebo test.
For the same 456 firms in our analysis sample, we identify all quarterly
earnings announcement dates (Compustat \texttt{rdq}) over the same 2001--2023
period, excluding any earnings announcement within 30 calendar days of an
auditor-change event to avoid contamination. This yields 20,800 placebo events.
We estimate a market model for each earnings event using the same methodology
as the main analysis (estimation window $[-252, -46]$ trading days, CRSP
value-weighted market return) and compute both $AbVol[-1,+1]$ and
$|CAR[-1,+1]|$.

Table~\ref{tab:placebo_8k} reports the results. Columns~(1)--(3) use
abnormal volume; columns~(4)--(6) use $|CAR|$. For AbVol, the
auditor-change baseline is $\beta = 0.111$ ($p < 0.01$, column~1), while
the earnings-announcement coefficient is $\beta = -0.010$ ($p > 0.10$,
column~2) --- a clean null with over 20,000 observations. The pooled
interaction (column~3) is $\beta = 0.141$ ($p < 0.01$), indicating that
the polarization effect on trading volume is significantly and
substantially larger for auditor-change disclosures than for earnings
announcements. The pattern is identical for $|CAR|$: a null placebo
coefficient ($\beta = -0.000$, $p > 0.10$, column~5) and a significant
pooled interaction ($\beta = 0.008$, $p < 0.01$, column~6). In both
cases, the base polarization coefficient in the pooled specification is
indistinguishable from zero, indicating that the entire effect is
concentrated in auditor changes.\footnote{The negative \textit{Auditor
Change} main effects ($-0.384$ for AbVol, $-0.024$ for $|CAR|$, both
$p < 0.01$) indicate that auditor-change events generate smaller average
market reactions than earnings announcements, consistent with the former
being less news-intensive than quarterly results.}

Earnings announcements carry unambiguous quantitative content --- the reported
EPS figure --- leaving far less room for politically shaped interpretation than
an auditor-change filing, which requires investors to evaluate auditor
credibility and infer the nature of the separation from limited disclosure. The
placebo null for both outcomes is consistent with the interpretation
channel: politically heterogeneous investors disagree specifically when the
signal is ambiguous, not when it is numerically precise.\footnote{%
We also tested whether the polarization effect is amplified among
firms where audit credibility is plausibly more salient --- financially
distressed firms (below-median Altman Z-score), firms with high discretionary
accruals (above-median Modified Jones model $|DA|$), and firms whose prior-year
audit opinion included a going-concern modification. None of these firm-level
interactions is statistically significant ($p > 0.35$ in all cases;
see Table~\ref{tab:audit_credibility} in Appendix~\ref{app:tables}),
consistent with the effect being driven by the state-level
political-information environment rather than by firm-specific accounting
quality concerns.}

\input{../Output/Tables/tab10_placebo_8k}

\subsection{Placebo Test: Officer-Change Disclosures}
\label{sec:placebo_502}

The earnings-announcement placebo is inconsistent with a generic salience explanation,
but it leaves open a tighter alternative: that polarization amplifies
reactions to \emph{any} mandatory 8-K filing requiring interpretation, not
specifically to audit-related disclosures. Form~8-K Item~5.02 officer-change
filings --- departures, elections, and appointments of directors and
certain officers --- provide the cleanest test of this alternative. Like
auditor-change filings, they are mandatory, standardized, and often require
investors to infer the nature of the change from limited disclosure
\citep{ghosh2015}. Unlike auditor-change filings, they do not involve
institutional trust in auditors or the PCAOB. If polarization effects are
driven by the institutional-trust channel that motivates our theory, they
should be larger for auditor changes than for officer changes from the
same firms.

We identify Item~5.02 filings by parsing the EDGAR full-text search index
for the Item~5.02 title phrase and extracting the relevant 8-K sections
with \texttt{edgarParser}. Restricting to the 456 firms in our analysis
sample and excluding events within 30 calendar days of the same firm's
auditor-change event yields 3,677 placebo events. We estimate a market
model for each event using the same methodology as the main analysis and
compute $AbVol[-1,+1]$ and $|CAR[-1,+1]|$.

Table~\ref{tab:placebo_502} reports the results in the same format as the
earnings-announcement placebo (Table~\ref{tab:placebo_8k}). The pattern
is consistent across both outcomes. For AbVol, the auditor-change baseline
is $\beta = 0.111$ ($p < 0.01$, column~1), while the officer-change
coefficient is $\beta = 0.016$ ($p > 0.10$, column~2). The pooled
interaction (column~3) is $\beta = 0.110$ ($p = 0.011$). For $|CAR|$, the
placebo coefficient is null ($\beta = -0.000$, $p > 0.10$, column~5) and
the pooled interaction is $\beta = 0.006$ ($p = 0.006$, column~6). Both
pooled interactions confirm that the polarization effect is significantly
and substantially larger for auditor-change disclosures than for
officer-change disclosures from the same firms --- a tighter specificity
test than the earnings placebo, because both event types are mandatory
8-K filings requiring interpretation from limited disclosure. The
pattern is consistent with the interpretation channel operating
specifically through institutional trust in auditors and regulatory
oversight, not through generic responses to ambiguous mandatory
disclosure.

\input{../Output/Tables/tab_placebo_502}

\subsection{Post-Event Price Persistence}
\label{sec:reversal}

If the polarization effect reflects short-lived overreaction --- noise
trading or attention-driven volume that washes out quickly --- then
post-event returns in high-polarization states should reverse. We test
this by regressing signed post-event CARs on polarization, controlling
for the event-window return. Specifically, we compute market-model CARs
over trading days $[+2,+20]$ (approximately one month) and $[+2,+60]$
(approximately three months) after the 8-K filing, using the same market
model parameters as the main analysis. We control for either the signed
$CAR(-1,+1)$ or $|CAR(-1,+1)|$ to partial out the mechanical tendency
of large initial reactions to mean-revert. Under the overreaction
hypothesis, the polarization coefficient should be negative: firms in
high-polarization states experience larger initial reactions that
subsequently unwind.

Table~\ref{tab:reversal} reports the results. In all four specifications,
the polarization coefficient is positive --- the opposite sign from
the overreaction prediction --- and not significant at conventional levels
(columns~1--2: $\beta = 0.013$, $p = 0.103$ and $\beta = 0.019$,
$p = 0.199$; columns~3--4 with $|CAR|$ control: $\beta = 0.014$,
$p = 0.088$ and $\beta = 0.019$, $p = 0.187$). Column~(3) is
marginally significant at the 10\% level, but the positive sign
indicates continuation rather than reversal. There is no evidence
of post-event price reversal in high-polarization states at either horizon.

This result is more consistent with persistent disagreement than with
transient overreaction. Under \citet{kandel1995}-style belief models,
investors who form different posteriors about firm quality after an
auditor change need not converge quickly, because their disagreement
stems from different priors about institutional credibility rather than
from a failure to process publicly available information. The absence of
reversal supports interpreting the main results as reflecting genuinely
heterogeneous valuations that persist beyond the event window, not
attention-driven noise that dissipates.

\input{../Output/Tables/tab09_reversal}

% ── 7. Conclusion ─────────────────────────────────────────────────────────────

\section{Conclusion}
\label{sec:conclusion}

This paper documents that auditor-change disclosures elicit stronger
disagreement-sensitive market reactions for firms headquartered in more
politically polarized states, consistent with heterogeneous interpretation
of credibility-sensitive audit disclosures. The volume
result is robust across alternative proxies and clustering structures; the return
result is directionally consistent but more fragile, as the disagreement
framework predicts. Two within-firm placebo tests --- on earnings announcements and on
Item~5.02 officer-change disclosures from the same firms --- suggest
that the association is specific to audit-credibility-sensitive disclosures,
not to any corporate news or any mandatory 8-K filing requiring
interpretation. Post-event returns show no reversal, consistent with
persistent disagreement rather than transient overreaction.

Several limitations
warrant emphasis. Headquarters-state polarization is a noisy reduced-form
proxy for the political-information environment of a geographically
dispersed investor base; measurement error of this kind attenuates
coefficients, but sharper identification of which investors drive the
pattern requires investor-level political data that we lack. The sample
($N = 678$) limits power for interaction tests, and our ambiguity indicator
conflates interpretive latitude with economic materiality, making it
difficult to isolate the pure ambiguity channel.

The findings suggest one limit to disclosure-based regulation in
credibility-sensitive settings: when investors differ in their assessments of
institutional trustworthiness, more disclosure does not eliminate disagreement.
As political polarization has increased persistently over the past two
decades \citep{iyengar2019, boxell2024, bertrand2023}, its effect on audit signal
interpretation may be growing. We study auditor changes as an
initial tractable setting, but the mechanism should operate wherever disclosure
interpretation depends on trust in regulated gatekeepers. Future research
should examine whether these patterns extend to critical audit matters, going
concern opinions, and internal control reports. Our supplementary test finds that national affective polarization
(ANES feeling-thermometer differential) does not add explanatory power
beyond ideological polarization (Table~\ref{tab:affective}), suggesting
the mechanism operates through the partisan composition of the local
electorate rather than time-varying partisan animus. However, the
national ANES measure is coarse; state- or investor-level measures of
affective polarization \citep{mason2015, druckmanlevy2021} could yield
different conclusions and remain a promising direction for future work.

\bibliographystyle{apalike}
\bibliography{references}

% ── Appendix ──────────────────────────────────────────────────────────────────

\appendix

\section{Supplementary Tables}
\label{app:tables}

\input{../Output/Tables/tab_supplementary}

\input{../Output/Tables/tab06_affective}

\input{../Output/Tables/tab10_audit_credibility}

\section{Proof of Proposition~\ref{prop:dispersion} and Additional Theoretical Results}
\label{app:proofs}

\noindent\textbf{Setup.} Let there be two investor groups, $D$ and $R$, with
population shares $\omega_D, \omega_R > 0$ and $\omega_D + \omega_R = 1$. Group $g$ holds prior
$\pi_g \in (0,1)$. The mean prior is $\bar{\pi} = \omega_D \pi_D + \omega_R \pi_R$.
After observing signal $s=1$, group $g$ holds posterior
$\phi(\pi_g)$, where the Bayesian updating function is
\[
    \phi(\pi) = \frac{p_H \pi}{p_H \pi + p_L(1-\pi)},
    \qquad p_H > p_L > 0.
\]
The function $\phi$ is strictly increasing and continuous on $(0,1)$.

\medskip
\noindent\textbf{Step 1: Variance formula.}
The posterior beliefs across groups follow a two-point distribution placing
mass $\omega_D$ at $\phi(\pi_D)$ and mass $\omega_R$ at $\phi(\pi_R)$. The population
mean posterior is $\bar{\phi} = \omega_D \phi(\pi_D) + \omega_R \phi(\pi_R)$. A
standard calculation gives:
\begin{align*}
    \mathrm{Var}[\phi(\pi_g)]
    &= \omega_D\bigl(\phi(\pi_D) - \bar\phi\bigr)^2
     + \omega_R\bigl(\phi(\pi_R) - \bar\phi\bigr)^2 \\
    &= \omega_D (\omega_R)^2 \bigl(\phi(\pi_D) - \phi(\pi_R)\bigr)^2
     + \omega_R (\omega_D)^2 \bigl(\phi(\pi_D) - \phi(\pi_R)\bigr)^2 \\
    &= \omega_D \omega_R (\omega_D + \omega_R) \bigl(\phi(\pi_D) - \phi(\pi_R)\bigr)^2 \\
    &= \omega_D \omega_R \bigl(\phi(\pi_D) - \phi(\pi_R)\bigr)^2,
\end{align*}
where the second equality uses $\phi(\pi_D) - \bar\phi = \omega_R(\phi(\pi_D) -
\phi(\pi_R))$ and $\phi(\pi_R) - \bar\phi = -\omega_D(\phi(\pi_D) - \phi(\pi_R))$,
and the last equality uses $\omega_D + \omega_R = 1$. This establishes the variance
formula in Proposition~\ref{prop:dispersion}.

\medskip
\noindent\textbf{Step 2: Monotonicity in $|\pi_D - \pi_R|$.}
Without loss of generality, assume $\pi_D > \pi_R$. A mean-preserving
spread that increases $|\pi_D - \pi_R|$ by $\epsilon > 0$ while holding
$\bar{\pi}$ fixed requires:
\[
    \pi_D' = \pi_D + \omega_R \epsilon, \qquad
    \pi_R' = \pi_R - \omega_D \epsilon,
\]
so that $\omega_D \pi_D' + \omega_R \pi_R' = \omega_D \pi_D + \omega_R \pi_R = \bar{\pi}$.
We restrict $\epsilon$ to be small enough that $\pi_D' \in (0,1)$ and
$\pi_R' \in (0,1)$; such $\epsilon > 0$ exists because $\pi_D, \pi_R \in
(0,1)$ strictly.

Since $\phi$ is strictly increasing:
\[
    \phi(\pi_D') = \phi(\pi_D + \omega_R\epsilon) > \phi(\pi_D),
    \qquad
    \phi(\pi_R') = \phi(\pi_R - \omega_D\epsilon) < \phi(\pi_R).
\]
Therefore:
\[
    \phi(\pi_D') - \phi(\pi_R')
    > \phi(\pi_D) - \phi(\pi_R) > 0.
\]
Since $\omega_D \omega_R > 0$ is unchanged, we conclude:
\[
    \mathrm{Var}[\phi(\pi_g')]
    = \omega_D \omega_R \bigl(\phi(\pi_D') - \phi(\pi_R')\bigr)^2
    > \omega_D \omega_R \bigl(\phi(\pi_D) - \phi(\pi_R)\bigr)^2
    = \mathrm{Var}[\phi(\pi_g)]. \qquad \square
\]

\medskip
\noindent\textbf{Remark (role of mean-preservation).}
The mean-preserving condition $\omega_D \pi_D' + \omega_R \pi_R' = \bar{\pi}$ is
used to hold the average prior fixed, ensuring that the comparison is
\emph{ceteris paribus}: only dispersion changes, not the level of the aggregate
belief. However, mean-preservation is \emph{sufficient}, not \emph{necessary},
for the variance to increase. The formula $\mathrm{Var}[\phi(\pi_g)] =
\omega_D \omega_R (\phi(\pi_D) - \phi(\pi_R))^2$ depends only on the gap
$|\phi(\pi_D) - \phi(\pi_R)|$, which is strictly increasing in $|\pi_D -
\pi_R|$ for any $\pi_D, \pi_R \in (0,1)$, regardless of what happens to the
mean. If affective polarization causes an asymmetric shift --- one group's prior
moves while the other's stays fixed --- the mean shifts too, but the posterior
variance still increases as long as the gap $|\pi_D - \pi_R|$ widens. The
mean-preserving restriction serves to isolate the dispersion effect from a
change in average pessimism or optimism, not to make the monotonicity result
logically possible.

\bigskip

\noindent\textbf{Proposition A1: Unified Channel Representation.}

\medskip
\noindent Let $\sigma(x) \equiv e^x/(1+e^x)$ denote the logistic map, with
$\sigma'(x) = \sigma(x)(1-\sigma(x)) > 0$ for all $x \in \mathbb{R}$.
For any prior $\pi \in (0,1)$, define prior log-odds $a(\pi) \equiv
\log[\pi/(1-\pi)]$ and objective log-likelihood ratio $\ell \equiv
\log(p_H/p_L) > 0$.

\begin{proposition}[Unified channel]
\label{prop:unified}
\label{prop:trust}
\label{prop:precision}
Let each group have posterior $\mu_g = \sigma(X_g)$, where the latent
log-odds index $X_g = a(\pi_g) + \tau_g \kappa_g \ell$ may differ across
groups through any combination of heterogeneous priors $\pi_g$, trust
$\tau_g \in [0,1]$, or perceived signal precision $\kappa_g > 0$.
When $\tau_g = \kappa_g = 1$ for all groups, $\sigma(X_g) = \phi(\pi_g)$,
the Bayesian posterior of Equation~\eqref{eq:bayes}, so the main model is
a special case. Then:
\[
    \mathrm{Var}(\mu_g) = \omega_D \omega_R \bigl[\sigma(X_D) - \sigma(X_R)\bigr]^2,
\]
and any mean-preserving spread of the latent indices --- increasing
$|X_D - X_R|$ while holding $\omega_D X_D + \omega_R X_R$ fixed --- strictly
increases $\mathrm{Var}(\mu_g)$.
In particular, if polarization widens the cross-group gap in any one of the
three underlying components via a mean-preserving spread --- prior log-odds,
trust, or perceived precision --- posterior variance and disagreement-sensitive
trading outcomes strictly increase.
\end{proposition}

\begin{proof}
The variance formula is the two-point distribution result (Step~1 above).
For the comparative static, consider $X_D' = X_D + \omega_R\epsilon$,
$X_R' = X_R - \omega_D\epsilon$ for $\epsilon > 0$, which preserves the
weighted mean. Since $\sigma$ is strictly increasing,
$\sigma(X_D') > \sigma(X_D)$ and $\sigma(X_R') < \sigma(X_R)$, so
$|\sigma(X_D')-\sigma(X_R')| > |\sigma(X_D)-\sigma(X_R)|$ and the variance
strictly increases. The same argument applies when the source of
heterogeneity is trust alone ($\pi$ and $\kappa$ common), precision alone
($\pi$ and $\tau$ common), or any combination --- in each case, the relevant
parameter enters $X_g$ monotonically, and a mean-preserving spread widens
the gap. $\square$
\end{proof}

\end{document}
